---
title: '[2025.03.09] Simulations'
author: "Anonymous"
date: "2024-09-09"
output: html_document
---

## Preliminaries

```{r}
library(dplyr)
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(sandwich)
library(readr)
library(lmtest)
```

# Load the data 

```{r}
data.2020 <- read.csv("data.ny.2020.csv")
data.2021    <- read.csv("data.ny.2021.csv")
data.2022   <- read.csv("data.ny.2022.csv")
data.2023       <- read.csv("data.ny.2023.csv")
data.2024   <- read.csv("data.ny.2024.csv")


# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2021 <- read_csv(
#   "data.ny.2021.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2022 <- read_csv(
#   "data.ny.2022.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2023 <- read_csv(
#   "data.ny.2023.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2024 <- read_csv(
#   "data.ny.2024.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )

# Combine the data 
data <- rbind(data.2020, data.2021, data.2022, data.2023, data.2024)


# # Debugging
# library(readr)
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# nrow(data.2020)
# problems(data.2020)

```


# Create the different varibles.

```{r}
# failure to appear
w <- toupper(trimws(data$Warrant_Ordered_btw_Arraign_and_Dispo))
d <- data$Release.Decision.at.Arraign == "Disposed at arraign"
data$fta_flag <- ifelse(d, NA_real_, ifelse(w == "Y", 1, ifelse(w == "N", 0, NA_real_)))

# release decisions
data <- data %>%
  mutate(release_v1 = ifelse(
    Release.Decision.at.Arraign == "ROR" | Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v1: defendant considered release iff they are released unconditionally or paid bail.

data <- data %>%
  mutate(release_v2 = ifelse(
    Release.Decision.at.Arraign %in% c("ROR", "Nonmonetary release") | # more lenient
      Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v2: defendant considered release iff they are released with or without conditions.

# Force NA when disposed at arraignment or unknown
data <- data %>%
  mutate(
    release_v1 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v1),
    release_v2 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v2)
  )

# # Force FTA to NA when defendant was not released under release_v1 
# data <- data %>%
#   mutate(
#     fta_flag = ifelse(release_v1 == 0, NA_real_, fta_flag)
#   )

# Set new data object
data.prelim <- data
```


# Remove cases with nominal $1 bail (often used to credit time served on a different case)
```{r}
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail
```


# Get bail-eligible charges vector and append to data (See the end of the file to see how this is done.)

```{r}
# load("[2026.03.10.1] qualifying.charges.any.RData") # old
load("[2026.05.02] qualifying.charges.any.RData")
data.prelim <- cbind(data.prelim, qualifying.charges.any)
```

# Further filtering based on qualifying vs. unqualifying charges. 
The default is to consider only bail-ineligible offenses. To restrict analysis to bail eligible offenses, set runn process_release(TRUE) instead of process_release()

```{r}
process_release <- function(filter_qualifying = FALSE) {
  
  if (filter_qualifying) {
    
    # Keep only qualifying charges
    data.prelim <<- data.prelim[data.prelim$qualifying.charges.any == 1, ]
    
  } else {
    # Force FTA to NA when defendant was not released under release_v1 - you *MAY* WANT TO COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
  data.prelim <- data.prelim %>%
    mutate(
      fta_flag = ifelse(release_v1 == 0, NA_real_, fta_flag)
    )
    
    # Set release_v2 = release_v1 for non-qualifying
    idx <- data.prelim$qualifying.charges.any == 0
    data.prelim$release_v2[idx] <<- data.prelim$release_v1[idx]
    
    # Keep only non-qualifying
    data.prelim <<- data.prelim[idx, ]
  }
}

# Non-Qualifying offenses
process_release()

# Qualifying offenses
# process_release(TRUE)
```

# Filter out judges who hear fewer than 100 cases

```{r}
# Filter out fewer than 100 cases. 
  ## get numbers
  judge_release_table.prelim <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
  ## judges with at least 100 cases (in the prelim table)
keep_judges <- judge_release_table.prelim %>%
  filter(n_cases >= 100) %>% # Standard
  # filter(n_cases >= 150) %>% # Robustness check - A.7
  # filter(n_cases >= 50) %>% # Robustness check - A.7
    pull(Judge_Name)

  ## filter data.prelim to only those judges
  data.prelim.100 <- data.prelim %>%
  filter(Judge_Name %in% keep_judges)
  
  ## complete the filtering
  data.prelim <- data.prelim.100
```

# Quasi-Random Assignment Balance Tables - A.2

```{r}
# --- 1. Create LOO ---
data.prelim <- data.prelim %>%
  dplyr::group_by(Judge_Name) %>%
  dplyr::mutate(
    n = sum(!is.na(release_v2)),
    s = sum(release_v2, na.rm = TRUE),
    loo_leniency = ifelse(!is.na(release_v2) & n > 1,
                          (s - release_v2) / (n - 1),
                          NA_real_)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::select(-n, -s)

# --- 2. Clean + FE variable ---
month_map <- c(Jan="01",Feb="02",Mar="03",Apr="04",May="05",Jun="06",
               Jul="07",Aug="08",Sep="09",Oct="10",Nov="11",Dec="12")

data.prelim$year_month <- paste0(trimws(data.prelim$Arrest.Year), "_",
                                 month_map[trimws(data.prelim$Arrest_Month)])

data.prelim$Age_at_Arrest <- as.numeric(trimws(data.prelim$Age_at_Arrest))
data.prelim$loo_leniency  <- as.numeric(trimws(data.prelim$loo_leniency))
data.prelim$any_prior <- as.numeric(
  (as.numeric(trimws(data.prelim$prior_misd_cnt)) +
   as.numeric(trimws(data.prelim$prior_nonvfo_cnt)) +
   as.numeric(trimws(data.prelim$prior_vfo_cnt))) > 0
)

# --- 3. Regression with court × month FE ---
results <- lm(
  loo_leniency ~
    I(Race == "White") +
    I(Gender == "Male") +
    Age_at_Arrest +
    I(Arraign.Charge.Category == "Drug") +
    I(Arraign.Charge.Category %in% c("DWI")) +
    I(Representation_at_Securing_Order == "Y") +
    any_prior +
    factor(interaction(Court_Name, year_month)),
  data = data.prelim
)

# --- 4. Two-way clustered SEs (individual + judge) ---
vcov_2way <- vcovCL(results,
                    cluster = data.prelim[, c("Judge_Name")])

# --- 5. Print only main coefficients with stars ---
ct <- coeftest(results, vcov = vcov_2way)
printCoefmat(ct[1:15, ], signif.stars = TRUE)

# F test

library(car)

joint_f_test <- linearHypothesis(
  results,
  c(
    'I(Race == "White")TRUE = 0',
    'I(Gender == "Male")TRUE = 0',
    'Age_at_Arrest = 0',
    'I(Arraign.Charge.Category == "Drug")TRUE = 0',
    'I(Arraign.Charge.Category %in% c("DWI"))TRUE = 0',
    'I(Representation_at_Securing_Order == "Y")TRUE = 0',
    'any_prior = 0'
  ),
  vcov. = vcov_2way,
  test = "F"
)

print(joint_f_test)
```

# Get judge info table

```{r}
judge_release_table <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(),
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  mutate(
    rank_v1 = min_rank(desc(pct_release_v1)),
    rank_v2 = min_rank(desc(pct_release_v2))
  ) %>%
  mutate(
    rank_diff = rank_v1 - rank_v2
  )

judge_fta_table <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    pct_fta = mean(fta_flag, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  mutate(
    rank_fta = min_rank(desc(pct_fta))
  )

judge.info.table.combined <- judge_release_table %>%
  inner_join(judge_fta_table, by = "Judge_Name") %>%
  mutate(
    rank_diff_v1_fta = rank_v1 - rank_fta,
    rank_diff_v2_fta = rank_v2 - rank_fta
  )

judge.info.table.combined
```

# Simulating Bootstrap outcomes based on judge

```{r}
set.seed(02138)

simulate_judge_rates <- function(judge_row, nsim = 2000, seed = NULL) {
  
  # optional seed
  # if (!is.null(seed)) set.seed(seed)
  
  # extract parameters
  N <- judge_row$n_cases
  p <- judge_row$pct_release_v2 / 100
  q <- judge_row$pct_fta / 100
  
  # multinomial probabilities
  prob_not_release   <- 1 - p
  prob_release_nofta <- p * (1 - q)
  prob_release_fta   <- p * q
  
  probs <- c(prob_not_release, prob_release_nofta, prob_release_fta)
  
  # simulate multinomial counts
  sim_counts <- t(rmultinom(n = nsim, size = N, prob = probs))
  colnames(sim_counts) <- c("C0_not_release", "C1_release_nofta", "C2_release_fta")
  
  sim_results <- as.data.frame(sim_counts) %>%
    dplyr::mutate(
      n_release = C1_release_nofta + C2_release_fta,
      release_rate_sim = n_release / N,
      fta_rate_sim = ifelse(n_release > 0, C2_release_fta / n_release, NA_real_)
    )
  
  return(sim_results)
}

# apply to all judges
sim_list <- setNames(
  lapply(1:nrow(judge.info.table.combined), function(i) {
    simulate_judge_rates(judge.info.table.combined[i, ], nsim = 2000)
  }),
  judge.info.table.combined$Judge_Name
)

# Simulation list save
# save(sim_list, file = "[2026.03.24] sim_list.RData")

```


# Counterfactual Analysis - A.8 [JM: TO FIX]

```{r}
# First get necessary data. 
library(dplyr)

# Get the most lenient judges for generation of counterfactual outcomes
judge_release <- data.prelim %>%
  filter(!is.na(release_v2)) %>%
  group_by(Judge_Name) %>%
  summarise(
    avg_release = mean(release_v2),
    n_cases = n(),
    .groups = "drop"
  )

cutoff <- quantile(judge_release$avg_release, 0.95)

top_judges <- judge_release %>%
  filter(avg_release >= cutoff) %>%
  arrange(desc(avg_release))

top_judges

# Filter the data so we only have cases associated with the most lenient judges
data.prelim_top <- data.prelim %>%
  filter(Judge_Name %in% top_judges$Judge_Name)

# Get the FTA rates by race for this group. 
fta_rates <- data.prelim_top %>%
  filter(release_v2 == 1) %>%
  mutate(
    race_group = ifelse(Race == "White", "White", "Non-White")
  ) %>%
  group_by(race_group) %>%
  summarise(
    avg_fta_rate = mean(fta_flag, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

fta_rates

# Code to compute d (false positives among detained)

mu <- 0.06

judge_false_positive_table <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(),
    
    a = mean(release_v2, na.rm = TRUE),                     # percent released
    b = mean(fta_flag[release_v2 == 1], na.rm = TRUE),      # FTA rate among released
    
    .groups = "drop"
  ) %>%
  mutate(
    c = 1 - a,
    
    q = (mu - a*b) / c,      # counterfactual FTA among detained
    
    d = 1 - q,               # false positives among detained
    
    d = pmax(pmin(d,1),0)    # force into [0,1]
  )

judge_false_positive_table

# Code to get predictive error for each judge: 
judge_false_positive_table <- judge_false_positive_table %>%
  mutate(
    predictive_error = a*b + c*d
  )

# Do the permutation analysis. 
run_analysis_counterfactual <- function(data = data.prelim, ...) {
  # Apply any number of filter conditions (all AND'ed together)
  data <- data %>% filter(...)

  # MAIN ANALYSIS
  judge_release_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
# judge_release_table

judge_release_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  ) %>%
  mutate(
    rank_v1 = min_rank(desc(pct_release_v1)),
    rank_v2 = min_rank(desc(pct_release_v2))
  )

judge_release_table <- judge_release_table %>%
  mutate(rank_diff = rank_v1 - rank_v2)

# Table of predictive error rates by judge
judge_fta_table <- judge_false_positive_table %>%
  select(Judge_Name, predictive_error) %>%
  mutate(
    pct_fta = predictive_error * 100
  ) %>%
  select(Judge_Name, pct_fta) %>%
  mutate(
    rank_fta = min_rank(desc(pct_fta))
  )

judge.info.table.combined <- cbind(judge_release_table, judge_fta_table[,2:3])

# Get the rank differences
judge.info.table.combined <- judge_release_table %>%
  inner_join(judge_fta_table, by = "Judge_Name") %>% 
  mutate(
    rank_diff_v1_fta = rank_v1 - rank_fta,
    rank_diff_v2_fta = rank_v2 - rank_fta
  )

# 1) Basic vector for convenience
rd <- judge.info.table.combined$rank_diff_v2_fta

# 2) Summary stats
v2_fta_rank_change_summary <- tibble(
  n               = sum(!is.na(rd)),
  mean_change     = mean(rd, na.rm = TRUE),
  mean_abs_change = mean(abs(rd), na.rm = TRUE),
  sd_change       = sd(rd, na.rm = TRUE),
  median_change   = median(rd, na.rm = TRUE),
  mad_change      = mad(rd, na.rm = TRUE),
  min_change      = min(rd, na.rm = TRUE),
  p10_change      = quantile(rd, 0.10, na.rm = TRUE, names = FALSE),
  p25_change      = quantile(rd, 0.25, na.rm = TRUE, names = FALSE),
  p75_change      = quantile(rd, 0.75, na.rm = TRUE, names = FALSE),
  p90_change      = quantile(rd, 0.90, na.rm = TRUE, names = FALSE),
  max_change      = max(rd, na.rm = TRUE),
  prop_positive   = mean(rd > 0, na.rm = TRUE),
  prop_negative   = mean(rd < 0, na.rm = TRUE),
  prop_zero       = mean(rd == 0, na.rm = TRUE)
)

# v2_fta_rank_change_summary %>% t()


# # 3) Top movers by absolute change
# top_movers_v2_fta <- judge.info.table.combined %>%
#   mutate(abs_diff_v2_fta = abs(rank_diff_v2_fta)) %>%
#   arrange(desc(abs_diff_v2_fta)) %>%
#   select(Judge_Name, rank_v2, rank_fta, rank_diff_v2_fta, abs_diff_v2_fta) %>%
#   slice_head(n = 20)

# top_movers_v2_fta

# 4) Density plot of rank changes (v2 vs FTA)
density.plot <- ggplot(judge.info.table.combined, aes(x = rank_diff_v2_fta)) +
  geom_density(na.rm = TRUE) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Density of Judge Rank Changes (Release v2 vs FTA)",
    x = "Rank Difference (rank_v2 - rank_fta)",
    y = "Density",
    caption = "Positive = judge ranks more release-lenient (v2) than FTA-heavy; Negative = the reverse"
  )

# Simple code for permutation test. Median.
# Returns the median absolute rank change (|rank_v2 - rank_fta|) after permuting rank_v2
# premtuation.test.function <- function(random.ranks) {
#   premuted.results <- judge.info.table.combined
#   stopifnot(length(random.ranks) == nrow(premuted.results))
# 
#   # replace rank_v2 with the supplied permutation
#   premuted.results$rank_v2 <- random.ranks
# 
#   # recompute the v2 vs FTA rank difference
#   premuted.results$rank_diff_v2_fta <- premuted.results$rank_v2 - premuted.results$rank_fta
# 
#   # return the median absolute change
#   median(abs(premuted.results$rank_diff_v2_fta), na.rm = TRUE)
# }
premtuation.test.function <- function(random.ranks) {
  permuted.results <- judge.info.table.combined
  stopifnot(length(random.ranks) == nrow(permuted.results))

  # replace rank_v2 with the supplied permutation
  permuted.results$rank_v2 <- random.ranks

  # return Kendall's tau between release-leniency rank and FTA rank
  cor(
    permuted.results$rank_v2,
    permuted.results$rank_fta,
    method = "kendall",
    use = "complete.obs"
  )
}

# set.seed(02138)

n.sim <- 10000   # number of random permutations
n.judges <- nrow(judge.info.table.combined)

# observed statistic
obs_stat <- median(abs(judge.info.table.combined$rank_diff_v2_fta), na.rm = TRUE)

# permutation distribution
perm_stats <- replicate(n.sim, {
  random_perm <- sample.int(n.judges, n.judges, replace = FALSE)
  premtuation.test.function(random_perm)
})

# summarize
resmedian <- tibble::tibble(
  observed = obs_stat,
  perm_mean = median(perm_stats),
  perm_sd = sd(perm_stats),
  p_value_right_tail = mean(perm_stats >= obs_stat)
)
# resmedian

# Simple code for permutation test. Mean.


# Returns the median absolute rank change (|rank_v2 - rank_fta|) after permuting rank_v2
# premtuation.test.function <- function(random.ranks) {
#   premuted.results <- judge.info.table.combined
#   stopifnot(length(random.ranks) == nrow(premuted.results))
# 
#   # replace rank_v2 with the supplied permutation
#   premuted.results$rank_v2 <- random.ranks
# 
#   # recompute the v2 vs FTA rank difference
#   premuted.results$rank_diff_v2_fta <- premuted.results$rank_v2 - premuted.results$rank_fta
# 
#   # return the median absolute change
#   mean(abs(premuted.results$rank_diff_v2_fta), na.rm = TRUE)
# }
premtuation.test.function <- function(random.ranks) {
  permuted.results <- judge.info.table.combined
  stopifnot(length(random.ranks) == nrow(permuted.results))

  # replace rank_v2 with the supplied permutation
  permuted.results$rank_v2 <- random.ranks

  # return Kendall's tau between release-leniency rank and FTA rank
  cor(
    permuted.results$rank_v2,
    permuted.results$rank_fta,
    method = "kendall",
    use = "complete.obs"
  )
}

# set.seed(02138)

n.sim <- 10000   # number of random permutations
n.judges <- nrow(judge.info.table.combined)

# observed statistic
obs_stat <- mean(abs(judge.info.table.combined$rank_diff_v2_fta), na.rm = TRUE)

# permutation distribution
perm_stats <- replicate(n.sim, {
  random_perm <- sample.int(n.judges, n.judges, replace = FALSE)
  premtuation.test.function(random_perm)
})

# summarize
resmean <- tibble::tibble(
  n.judges = n.judges,
  observed = obs_stat,
  perm_mean = mean(perm_stats),
  perm_sd = sd(perm_stats),
  # p_value_right_tail = mean(perm_stats >= obs_stat)
  p_value_right_tail = 1 - mean(perm_stats >= obs_stat)
)
# resmean 


summary.stats <- judge.info.table.combined %>%
  summarise(
    pct_fta_p25 = quantile(pct_fta, 0.25, na.rm = TRUE),
    pct_fta_median = median(pct_fta, na.rm = TRUE),
    pct_fta_p75 = quantile(pct_fta, 0.75, na.rm = TRUE),
    
    pct_release_v2_p25 = quantile(pct_release_v2, 0.25, na.rm = TRUE),
    pct_release_v2_median = median(pct_release_v2, na.rm = TRUE),
    pct_release_v2_p75 = quantile(pct_release_v2, 0.75, na.rm = TRUE),
    
    kendall_tau = cor(pct_release_v2, pct_fta, method = "kendall", use = "complete.obs") # 202.03.07 adding kendall tau

  )

# summary.stats

results <- list(judge.info.table.combined = judge.info.table.combined, v2_fta_rank_change_summary = v2_fta_rank_change_summary, 
                # top_movers_v2_fta = top_movers_v2_fta, 
                resmean = resmean, summary.stats = summary.stats, perm_stats = perm_stats, density.plot = density.plot)
  # -----------------------------------

  return(results)
}

# Conduct the Analysis
# Overall sample
results.overall <- run_analysis_counterfactual(data = data.prelim, TRUE)

# Print the result
# Define the list of result objects
all_results <- list(
  Overall = results.overall
  # ,
  # White = results.white,
  # `Non-White` = results.nonwhite,
  # Misdemeanor = results.mis,
  # Felony = results.fel,
  # `With Rep.` = results.rep,
  # `No Rep.` = results.norep
)

# Loop and print the quantities for each
for (name in names(all_results)) {
  res <- all_results[[name]]
  
  if (!is.null(res$resmean)) {
    cat("\n----", name, "----\n")
    cat("p-value:", signif(res$resmean$p_value_right_tail, 3), "\n")
    cat("Avg. Abs. Rank Diff.:", round(res$resmean$observed, 2), "\n")
    cat("Mean Under Null:", round(res$resmean$perm_mean, 2), "\n")
    cat("SD Under Null:", round(res$resmean$perm_sd, 2), "\n")
    
    rho <- cor(
      res$judge.info.table.combined$rank_v2,
      res$judge.info.table.combined$rank_fta,
      method = "spearman",
      use = "complete.obs"
    )
    cat("Spearman's rho:", round(rho, 3), "\n")
    # NEW: print Kendall tau
    cat("Kendall's tau:", round(res$summary.stats$kendall_tau, 3), "\n")
    cat("# Judges:", res$resmean$n.judges, "\n")
  }
}
```

# Bootstrap diagnostics [optional]

```{r eval=FALSE, include=FALSE}
library(dplyr)
# --- core bootstrap function for ONE judge ---
bootstrap_one_judge <- function(judge_name, data, B = 100, prop = 0.6) {
  
  # subset data for this judge
  df_judge <- data %>%
    filter(Judge_Name == judge_name)
  
  n <- nrow(df_judge)
  
  # handle edge case
  if (n == 0) {
    return(rep(NA, 2 * B))
  }
  
  sample_size <- ceiling(prop * n)
  
  # storage: strictness + reappearance for each bootstrap
  out <- numeric(2 * B)
  
  for (b in seq_len(B)) {
    
    # bootstrap sample with replacement
    idx <- sample.int(n, size = sample_size, replace = TRUE)
    df_boot <- df_judge[idx, ]
    
    # --- strictness (release rate) ---
    strictness <- mean(df_boot$release_v1, na.rm = TRUE)
    
    # --- reappearance ---
    # assuming fta_flag = 1 means FTA (bad), 0 means reappeared
    # so reappearance rate = 1 - mean(fta_flag)
    reappearance <- 1 - mean(df_boot$fta_flag, na.rm = TRUE)
    
    # store
    out[2*b - 1] <- strictness
    out[2*b]     <- reappearance
  }
  
  return(out)
}


# --- wrapper over all judges ---
bootstrap_all_judges <- function(data, B = 100, prop = 0.6) {
  
  judges <- unique(data$Judge_Name)
  
  # apply bootstrap to each judge
  res_list <- lapply(judges, function(j) {
    bootstrap_one_judge(j, data, B = B, prop = prop)
  })
  
  # combine into matrix
  res_mat <- do.call(rbind, res_list)
  
  # name rows
  rownames(res_mat) <- judges
  
  # name columns: strict_1, reappear_1, strict_2, reappear_2, ...
  col_names <- unlist(lapply(seq_len(B), function(b) {
    c(paste0("strict_", b), paste0("reappear_", b))
  }))
  
  colnames(res_mat) <- col_names
  
  # convert to data frame and add judge name column
  res_df <- as.data.frame(res_mat)
  res_df$Judge_Name <- judges
  
  # move Judge_Name to front
  res_df <- res_df %>%
    select(Judge_Name, everything())
  
  return(res_df)
}


# --- RUN IT ---
bootstrap_results <- bootstrap_all_judges(
  data = data.prelim,
  B = 100,     # number of bootstrap draws
  prop = 0.6   # 60% sampling
)


# Sanity check for bootstrap
# --- identify bootstrap columns ---
strict_cols <- grep("^strict_", names(bootstrap_results))
reappear_cols <- grep("^reappear_", names(bootstrap_results))

# --- compute bootstrap means ---
bootstrap_summary <- data.frame(
  Judge_Name = bootstrap_results$Judge_Name,
  boot_mean_strict = rowMeans(bootstrap_results[, strict_cols], na.rm = TRUE),
  boot_mean_reappear = rowMeans(bootstrap_results[, reappear_cols], na.rm = TRUE)
)

# --- true values from original table ---
true_values <- judge.info.table.combined %>%
  transmute(
    Judge_Name,
    true_strict = pct_release_v1 / 100,
    true_reappear = 1 - (pct_fta / 100)
  )

# --- merge and compute differences ---
comparison <- bootstrap_summary %>%
  left_join(true_values, by = "Judge_Name") %>%
  mutate(
    diff_strict = boot_mean_strict - true_strict,
    diff_reappear = boot_mean_reappear - true_reappear
  )

# --- summaries ---
print(summary(comparison$diff_strict))
print(summary(comparison$diff_reappear))

print(mean(abs(comparison$diff_strict), na.rm = TRUE))
print(mean(abs(comparison$diff_reappear), na.rm = TRUE))

# --- worst discrepancies ---
print(
  comparison %>%
    arrange(desc(abs(diff_strict))) %>%
    select(Judge_Name, diff_strict) %>%
    head()
)

print(
  comparison %>%
    arrange(desc(abs(diff_reappear))) %>%
    select(Judge_Name, diff_reappear) %>%
    head()
)

# --- plots ---
par(mfrow = c(1,2))

plot(comparison$true_strict, comparison$boot_mean_strict,
     main = "Strictness: True vs Bootstrap",
     xlab = "True", ylab = "Bootstrap Mean")
abline(0, 1, col = "red")

plot(comparison$true_reappear, comparison$boot_mean_reappear,
     main = "Reappearance: True vs Bootstrap",
     xlab = "True", ylab = "Bootstrap Mean")
abline(0, 1, col = "red")

# --- histograms of bias ---
par(mfrow = c(1,2))

hist(comparison$diff_strict, main = "Bias in Strictness", breaks = 30)
hist(comparison$diff_reappear, main = "Bias in Reappearance", breaks = 30)

```

# Functional approach to analysis [Kendall Tau] - Table 3 and A.10

```{r}
run_analysis <- function(data = data.prelim, ...) {
  # Apply any number of filter conditions (all AND'ed together)
  data <- data %>% filter(...)

  # MAIN ANALYSIS
  judge_release_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
# judge_release_table

judge_release_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  ) %>%
  mutate(
    rank_v1 = min_rank(desc(pct_release_v1)),
    rank_v2 = min_rank(desc(pct_release_v2))
  )

judge_release_table <- judge_release_table %>%
  mutate(rank_diff = rank_v1 - rank_v2)

# judge_release_table

# Table of FTA rates by judge
judge_fta_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    pct_fta = mean(fta_flag, na.rm = TRUE) * 100
  ) %>%
  mutate(
    rank_fta = min_rank(desc(pct_fta))
  )

# judge_fta_table

judge.info.table.combined <- cbind(judge_release_table, judge_fta_table[,2:3])

# judge.info.table.combined


# Get the rank differences
judge.info.table.combined <- judge_release_table %>%
  inner_join(judge_fta_table, by = "Judge_Name") %>% 
  mutate(
    rank_diff_v1_fta = rank_v1 - rank_fta,
    rank_diff_v2_fta = rank_v2 - rank_fta
  )

# 1) Basic vector for convenience
rd <- judge.info.table.combined$rank_diff_v2_fta

# 2) Summary stats
v2_fta_rank_change_summary <- tibble(
  n               = sum(!is.na(rd)),
  mean_change     = mean(rd, na.rm = TRUE),
  mean_abs_change = mean(abs(rd), na.rm = TRUE),
  sd_change       = sd(rd, na.rm = TRUE),
  median_change   = median(rd, na.rm = TRUE),
  mad_change      = mad(rd, na.rm = TRUE),
  min_change      = min(rd, na.rm = TRUE),
  p10_change      = quantile(rd, 0.10, na.rm = TRUE, names = FALSE),
  p25_change      = quantile(rd, 0.25, na.rm = TRUE, names = FALSE),
  p75_change      = quantile(rd, 0.75, na.rm = TRUE, names = FALSE),
  p90_change      = quantile(rd, 0.90, na.rm = TRUE, names = FALSE),
  max_change      = max(rd, na.rm = TRUE),
  prop_positive   = mean(rd > 0, na.rm = TRUE),
  prop_negative   = mean(rd < 0, na.rm = TRUE),
  prop_zero       = mean(rd == 0, na.rm = TRUE)
)

# v2_fta_rank_change_summary %>% t()


# # 3) Top movers by absolute change
# top_movers_v2_fta <- judge.info.table.combined %>%
#   mutate(abs_diff_v2_fta = abs(rank_diff_v2_fta)) %>%
#   arrange(desc(abs_diff_v2_fta)) %>%
#   select(Judge_Name, rank_v2, rank_fta, rank_diff_v2_fta, abs_diff_v2_fta) %>%
#   slice_head(n = 20)

# top_movers_v2_fta

# 4) Density plot of rank changes (v2 vs FTA)
density.plot <- ggplot(judge.info.table.combined, aes(x = rank_diff_v2_fta)) +
  geom_density(na.rm = TRUE) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Density of Judge Rank Changes (Release v2 vs FTA)",
    x = "Rank Difference (rank_v2 - rank_fta)",
    y = "Density",
    caption = "Positive = judge ranks more release-lenient (v2) than FTA-heavy; Negative = the reverse"
  )

# Simple code for permutation test. Median.
# Returns the median absolute rank change (|rank_v2 - rank_fta|) after permuting rank_v2
# premtuation.test.function <- function(random.ranks) {
#   premuted.results <- judge.info.table.combined
#   stopifnot(length(random.ranks) == nrow(premuted.results))
# 
#   # replace rank_v2 with the supplied permutation
#   premuted.results$rank_v2 <- random.ranks
# 
#   # recompute the v2 vs FTA rank difference
#   premuted.results$rank_diff_v2_fta <- premuted.results$rank_v2 - premuted.results$rank_fta
# 
#   # return the median absolute change
#   median(abs(premuted.results$rank_diff_v2_fta), na.rm = TRUE)
# }
premtuation.test.function <- function(random.ranks) {
  permuted.results <- judge.info.table.combined
  stopifnot(length(random.ranks) == nrow(permuted.results))

  # replace rank_v2 with the supplied permutation
  permuted.results$rank_v2 <- random.ranks

  # return Kendall's tau between release-leniency rank and FTA rank
  cor(
    permuted.results$rank_v2,
    permuted.results$rank_fta,
    method = "kendall",
    use = "complete.obs"
  )
}

# set.seed(02138)

n.sim <- 5000   # number of random permutations
n.judges <- nrow(judge.info.table.combined)

# observed statistic
obs_stat <- median(abs(judge.info.table.combined$rank_diff_v2_fta), na.rm = TRUE) %>% abs

# permutation distribution
perm_stats <- replicate(n.sim, {
  random_perm <- sample.int(n.judges, n.judges, replace = FALSE)
  premtuation.test.function(random_perm)
}) %>% abs

# summarize
resmedian <- tibble::tibble(
  observed = obs_stat,
  perm_mean = median(perm_stats),
  perm_sd = sd(perm_stats),
  p_value_right_tail = mean(perm_stats >= obs_stat)
)
# resmedian

# Simple code for permutation test. Mean.
# # Returns the median absolute rank change (|rank_v2 - rank_fta|) after permuting rank_v2
# premtuation.test.function <- function(random.ranks) {
#   premuted.results <- judge.info.table.combined
#   stopifnot(length(random.ranks) == nrow(premuted.results))
# 
#   # replace rank_v2 with the supplied permutation
#   premuted.results$rank_v2 <- random.ranks
# 
#   # recompute the v2 vs FTA rank difference
#   premuted.results$rank_diff_v2_fta <- premuted.results$rank_v2 - premuted.results$rank_fta
# 
#   # return the median absolute change
#   mean(abs(premuted.results$rank_diff_v2_fta), na.rm = TRUE)
# }
# Returns Kendall's tau between rank_v2 and rank_fta after permuting rank_v2
premtuation.test.function <- function(random.ranks) {
  permuted.results <- judge.info.table.combined
  stopifnot(length(random.ranks) == nrow(permuted.results))

  # replace rank_v2 with the supplied permutation
  permuted.results$rank_v2 <- random.ranks

  # compute Kendall's tau
  cor(
    permuted.results$rank_v2,
    permuted.results$rank_fta,
    method = "kendall",
    use = "complete.obs"
  )
}

# set.seed(02138)

n.sim <- 5000   # number of random permutations
n.judges <- nrow(judge.info.table.combined)

# observed statistic
obs_stat <- cor(
  judge.info.table.combined$rank_v2,
  judge.info.table.combined$rank_fta,
  method = "kendall",
  use = "complete.obs"
) %>% abs

# permutation distribution
perm_stats <- replicate(n.sim, {
  random_perm <- sample.int(n.judges, n.judges, replace = FALSE)
  premtuation.test.function(random_perm)
}) %>% abs

# summarize
resmean <- tibble::tibble(
  n.judges = n.judges,
  observed = obs_stat,
  perm_mean = mean(perm_stats),
  perm_sd = sd(perm_stats),
  # p_value_right_tail = mean(perm_stats >= obs_stat)
  p_value_right_tail = mean(perm_stats >= obs_stat)
)
# resmean 


summary.stats <- judge.info.table.combined %>%
  summarise(
    pct_fta_p25 = quantile(pct_fta, 0.25, na.rm = TRUE),
    pct_fta_median = median(pct_fta, na.rm = TRUE),
    pct_fta_p75 = quantile(pct_fta, 0.75, na.rm = TRUE),
    
    pct_release_v2_p25 = quantile(pct_release_v2, 0.25, na.rm = TRUE),
    pct_release_v2_median = median(pct_release_v2, na.rm = TRUE),
    pct_release_v2_p75 = quantile(pct_release_v2, 0.75, na.rm = TRUE),
    
    kendall_tau = cor(pct_release_v2, pct_fta, method = "kendall", use = "complete.obs") # 202.03.07 adding kendall tau

  )

# summary.stats

results <- list(judge.info.table.combined = judge.info.table.combined, v2_fta_rank_change_summary = v2_fta_rank_change_summary, 
                # top_movers_v2_fta = top_movers_v2_fta, 
                resmean = resmean, summary.stats = summary.stats, perm_stats = perm_stats, density.plot = density.plot)
  # -----------------------------------

  return(results)
}
```


# Conduct Analysis

```{r}
# Set seed 
set.seed(02138)

# Overall sample
results.overall <- run_analysis(data = data.prelim, TRUE)
# 
# # Race
# results.white    <- run_analysis(data = data.prelim, Race == "White")
# results.nonwhite <- run_analysis(data = data.prelim, Race != "White" & Race != "Unknown")
# 
# # Severity of Charge
# results.mis <- run_analysis(data = data.prelim, Top_Severity_at_Arraign == "Misdemeanor")
# results.fel <- run_analysis(data = data.prelim, Top_Severity_at_Arraign == "Felony")
# 
# # Representation
# results.rep    <- run_analysis(data = data.prelim, Representation_at_Securing_Order == "Y")
# results.norep  <- run_analysis(data = data.prelim, Representation_at_Securing_Order == "N")

```


# Print all  analyses

```{r}
# Define the list of result objects
all_results <- list(
  Overall = results.overall
  # ,
  # White = results.white,
  # `Non-White` = results.nonwhite,
  # Misdemeanor = results.mis,
  # Felony = results.fel,
  # `With Rep.` = results.rep,
  # `No Rep.` = results.norep
)

# Loop and print the quantities for each
for (name in names(all_results)) {
  res <- all_results[[name]]
  
  if (!is.null(res$resmean)) {
    cat("\n----", name, "----\n")
    cat("p-value:", signif(res$resmean$p_value_right_tail, 3), "\n")
    cat("Avg. Abs. Rank Diff.:", round(res$resmean$observed, 2), "\n")
    cat("Mean Under Null:", round(res$resmean$perm_mean, 2), "\n")
    cat("SD Under Null:", round(res$resmean$perm_sd, 2), "\n")
    
    rho <- cor(
      res$judge.info.table.combined$rank_v2,
      res$judge.info.table.combined$rank_fta,
      method = "spearman",
      use = "complete.obs"
    )
    cat("Spearman's rho:", round(rho, 3), "\n")
    # NEW: print Kendall tau
    cat("Kendall's tau:", round(res$summary.stats$kendall_tau, 3), "\n")
    cat("# Judges:", res$resmean$n.judges, "\n")
  }
}
```

# Basic linear regressions - A.3

```{r}
run_analysis_ols <- function(data = data.prelim, ...) {
  # Apply any number of filter conditions (all AND'ed together)
  data <- data %>% filter(...)

  # MAIN ANALYSIS
  judge_release_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )

# judge_release_table

judge_release_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  ) %>%
  mutate(
    rank_v1 = min_rank(desc(pct_release_v1)),
    rank_v2 = min_rank(desc(pct_release_v2))
  )

judge_release_table <- judge_release_table %>%
  mutate(rank_diff = rank_v1 - rank_v2)

# judge_release_table

# Table of FTA rates by judge
judge_fta_table <- data %>%
  group_by(Judge_Name) %>%
  summarise(
    pct_fta = mean(fta_flag, na.rm = TRUE) * 100
  ) %>%
  mutate(
    rank_fta = min_rank(desc(pct_fta))
  )

# judge_fta_table

judge.info.table.combined <- cbind(judge_release_table, judge_fta_table[,2:3])

# judge.info.table.combined

  # simple linear regression: pct_fta ~ pct_release_v2
  model <- lm(pct_fta ~ pct_release_v2, data = judge.info.table.combined)
  
  # extract key results
  summary_model <- summary(model)
  coef_table <- summary_model$coefficients
  
  # organize outputs
  results <- list(
    coefficients = coef_table,
    intercept = coef(model)[1],
    slope = coef(model)[2],
    r_squared = summary_model$r.squared,
    adj_r_squared = summary_model$adj.r.squared,
    p_value = coef_table[2, 4],
    model_summary = summary_model
  )
  
  return(results)
  }

```

## conuct the basic linear regression analysis

```{r}
# Overall sample
results.overall.ols <- run_analysis_ols(data = data.prelim, TRUE)

# Race
results.white.ols    <- run_analysis_ols(data = data.prelim, Race == "White")
results.nonwhite.ols <- run_analysis_ols(data = data.prelim, Race != "White" & Race != "Unknown")

# Severity of Charge
results.mis.ols <- run_analysis_ols(data = data.prelim, Top_Severity_at_Arraign == "Misdemeanor")
results.fel.ols <- run_analysis_ols(data = data.prelim, Top_Severity_at_Arraign == "Felony")

# Representation
results.rep.ols    <- run_analysis_ols(data = data.prelim, Representation_at_Securing_Order == "Y")
results.norep.ols  <- run_analysis_ols(data = data.prelim, Representation_at_Securing_Order == "N")

# Bundle all OLS results into one named list
all_ols_results <- list(
  overall  = results.overall.ols,
  white    = results.white.ols,
  nonwhite = results.nonwhite.ols,
  mis      = results.mis.ols,
  fel      = results.fel.ols,
  rep      = results.rep.ols,
  norep    = results.norep.ols
)

```

## Print the results

```{r}
# Function to safely extract coefficient info (fixed version)
extract_ols_info <- function(res) {
  if (is.null(res$coefficients)) return(NULL)
  slope <- res$coefficients["pct_release_v2", "Estimate"]
  se_slope <- res$coefficients["pct_release_v2", "Std. Error"]
  intercept <- res$coefficients["(Intercept)", "Estimate"]
  se_intercept <- res$coefficients["(Intercept)", "Std. Error"]
  r2 <- res$r_squared
  adjr2 <- res$adj_r_squared
  
  # Extract n from model_summary if it exists, else set NA
  n <- tryCatch({
    as.numeric(gsub(".* on ([0-9]+) degrees of freedom.*", "\\1", 
                    capture.output(res$model_summary)[grep("degrees of freedom", capture.output(res$model_summary))][1])) + 2
  }, error = function(e) NA)
  
  return(list(
    slope = slope,
    se_slope = se_slope,
    intercept = intercept,
    se_intercept = se_intercept,
    r2 = r2,
    adjr2 = adjr2,
    n = n
  ))
}

# Loop through and print each
for (name in names(all_ols_results)) {
  res <- extract_ols_info(all_ols_results[[name]])
  if (!is.null(res)) {
    cat("\n----", name, "----\n")
    cat("Slope:", round(res$slope, 3), "\n")
    cat("SE (slope):", round(res$se_slope, 3), "\n")
    cat("Intercept:", round(res$intercept, 3), "\n")
    cat("SE (intercept):", round(res$se_intercept, 3), "\n")
    cat("R²:", round(res$r2, 3), "\n")
    cat("Adj. R²:", round(res$adjr2, 3), "\n")
    cat("Judges:", res$n, "\n")
  }
}

```

# logit A.4. 

```{r}
run_analysis_logit <- function(data = data.prelim, ...) {

  # Apply filters
  data <- data %>% filter(...)

  # Compute judge strictness (release rate)
  judge_release_table <- data %>%
    group_by(Judge_Name) %>%
    summarise(
      pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
    )

  # Merge strictness back to individual observations
  data <- data %>%
    left_join(judge_release_table, by = "Judge_Name")

  # Logistic regression: FTA ~ judge strictness
  model <- glm(fta_flag ~ pct_release_v2,
               data = data,
               family = binomial(link = "logit"))

  # summary_model <- summary(model)
  # coef_table <- summary_model$coefficients


cluster_se <- vcovCL(model, cluster = data$Judge_Name)
coef_table <- coeftest(model, vcov = cluster_se)

summary_model <- summary(model)

  # results <- list(
  #   coefficients = coef_table,
  #   intercept = coef(model)[1],
  #   slope = coef(model)[2],
  #   p_value = coef_table[2,4],
  #   model_summary = summary_model
  # )

results <- list(
  coefficients = coef_table,
  intercept = coef(model)[1],
  slope = coef(model)[2],
  p_value = coef_table[2,4],
  n = nobs(model),
  model_summary = summary_model
)

  return(results)
}
```


## conduct basic probit and print results

```{r}
# conduct the basic logit regression analysis

# Overall sample
results.overall.logit <- run_analysis_logit(data = data.prelim, TRUE)

# Race
results.white.logit    <- run_analysis_logit(data = data.prelim, Race == "White")
results.nonwhite.logit <- run_analysis_logit(data = data.prelim, Race != "White" & Race != "Unknown")

# Severity of Charge
results.mis.logit <- run_analysis_logit(data = data.prelim, Top_Severity_at_Arraign == "Misdemeanor")
results.fel.logit <- run_analysis_logit(data = data.prelim, Top_Severity_at_Arraign == "Felony")

# Representation
results.rep.logit    <- run_analysis_logit(data = data.prelim, Representation_at_Securing_Order == "Y")
results.norep.logit  <- run_analysis_logit(data = data.prelim, Representation_at_Securing_Order == "N")

# Bundle all logit results
all_logit_results <- list(
  overall  = results.overall.logit,
  white    = results.white.logit,
  nonwhite = results.nonwhite.logit,
  mis      = results.mis.logit,
  fel      = results.fel.logit,
  rep      = results.rep.logit,
  norep    = results.norep.logit
)

extract_logit_info <- function(res) {

  if (is.null(res$coefficients)) return(NULL)

  slope <- res$coefficients["pct_release_v2", "Estimate"]
  se_slope <- res$coefficients["pct_release_v2", "Std. Error"]

  intercept <- res$coefficients["(Intercept)", "Estimate"]
  se_intercept <- res$coefficients["(Intercept)", "Std. Error"]

  p_value <- res$coefficients["pct_release_v2", "Pr(>|z|)"]

  n <- res$n   # <-- use the stored sample size

  list(
    slope = slope,
    se_slope = se_slope,
    intercept = intercept,
    se_intercept = se_intercept,
    p_value = p_value,
    n = n
  )
}

for (name in names(all_logit_results)) {

  res <- extract_logit_info(all_logit_results[[name]])

  if (!is.null(res)) {
    cat("\n----", name, "----\n")
    cat("Slope (log-odds):", round(res$slope, 3), "\n")
    cat("SE (slope):", round(res$se_slope, 3), "\n")
    cat("Intercept:", round(res$intercept, 3), "\n")
    cat("SE (intercept):", round(res$se_intercept, 3), "\n")
    cat("p-value:", round(res$p_value, 4), "\n")
    cat("Observations:", res$n, "\n")
  }

}
```


# Probit A.5

```{r}
run_analysis_probit <- function(data = data.prelim, ...) {

  # Apply filters
  data <- data %>% filter(...)

  # Compute judge strictness (release rate)
  judge_release_table <- data %>%
    group_by(Judge_Name) %>%
    summarise(
      pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
    )

  # Merge strictness back to individual observations
  data <- data %>%
    left_join(judge_release_table, by = "Judge_Name")

  # Probit regression: FTA ~ judge strictness
  model <- glm(
    fta_flag ~ pct_release_v2,
    data = data,
    family = binomial(link = "probit")
  )

  summary_model <- summary(model)
  coef_table <- summary_model$coefficients

  results <- list(
    coefficients = coef_table,
    intercept = coef(model)[1],
    slope = coef(model)[2],
    p_value = coef_table[2,4],
    model_summary = summary_model
  )

  return(results)
}
```


## Run and print

```{r}
# conduct the basic probit regression analysis

# Overall sample
results.overall.probit <- run_analysis_probit(data = data.prelim, TRUE)

# Race
results.white.probit    <- run_analysis_probit(data = data.prelim, Race == "White")
results.nonwhite.probit <- run_analysis_probit(data = data.prelim, Race != "White" & Race != "Unknown")

# Severity of Charge
results.mis.probit <- run_analysis_probit(data = data.prelim, Top_Severity_at_Arraign == "Misdemeanor")
results.fel.probit <- run_analysis_probit(data = data.prelim, Top_Severity_at_Arraign == "Felony")

# Representation
results.rep.probit    <- run_analysis_probit(data = data.prelim, Representation_at_Securing_Order == "Y")
results.norep.probit  <- run_analysis_probit(data = data.prelim, Representation_at_Securing_Order == "N")

# Bundle all probit results
all_probit_results <- list(
  overall  = results.overall.probit,
  white    = results.white.probit,
  nonwhite = results.nonwhite.probit,
  mis      = results.mis.probit,
  fel      = results.fel.probit,
  rep      = results.rep.probit,
  norep    = results.norep.probit
)

all_probit_results
```

# pearson - A.6

```{r}
run_analysis_correlation <- function(data = data.prelim, ...) {
  
  # Apply filters
  data <- data %>% filter(...)
  
  # Judge strictness (release rates)
  judge_release_table <- data %>%
    group_by(Judge_Name) %>%
    summarise(
      pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
    )
  
  # Judge FTA rates
  judge_fta_table <- data %>%
    group_by(Judge_Name) %>%
    summarise(
      pct_fta = mean(fta_flag, na.rm = TRUE) * 100
    )
  
  # Merge tables
  judge.info.table.combined <- cbind(judge_release_table, judge_fta_table[,2])
  colnames(judge.info.table.combined)[3] <- "pct_fta"
  
  # Convert to re-appearance rate
  judge.info.table.combined <- judge.info.table.combined %>%
    mutate(pct_reappearance = 100 - pct_fta)
  
  # Pearson correlation test
  corr_test <- cor.test(
    judge.info.table.combined$pct_release_v2,
    judge.info.table.combined$pct_reappearance,
    method = "pearson"
  )
  
  results <- list(
    correlation = corr_test$estimate,
    p_value = corr_test$p.value,
    conf_int = corr_test$conf.int,
    test_object = corr_test
  )
  
  return(results)
}
```

## run and print

```{r}
# conduct the Pearson correlation analysis

# Overall sample
results.overall.corr <- run_analysis_correlation(data = data.prelim, TRUE)

# Race
results.white.corr    <- run_analysis_correlation(data = data.prelim, Race == "White")
results.nonwhite.corr <- run_analysis_correlation(data = data.prelim, Race != "White" & Race != "Unknown")

# Severity of Charge
results.mis.corr <- run_analysis_correlation(data = data.prelim, Top_Severity_at_Arraign == "Misdemeanor")
results.fel.corr <- run_analysis_correlation(data = data.prelim, Top_Severity_at_Arraign == "Felony")

# Representation
results.rep.corr    <- run_analysis_correlation(data = data.prelim, Representation_at_Securing_Order == "Y")
results.norep.corr  <- run_analysis_correlation(data = data.prelim, Representation_at_Securing_Order == "N")

# Bundle all correlation results
all_corr_results <- list(
  overall  = results.overall.corr,
  white    = results.white.corr,
  nonwhite = results.nonwhite.corr,
  mis      = results.mis.corr,
  fel      = results.fel.corr,
  rep      = results.rep.corr,
  norep    = results.norep.corr
)
all_corr_results
```

# Code for partial ordering analysis. 

# get the data

```{r}
# Sort the judge info table by number of cases (ascending)
sorted_table <- results.overall$judge.info.table.combined %>%
  arrange(n_cases)

# Display the first few rows to verify

top10_judges <- results.overall$judge.info.table.combined %>%
  arrange(desc(n_cases)) %>%
  # slice(1:5) # For top 5 
  # slice(1:10) #  For top 10 
# slice(1:20) #  For top 20
 slice(1:nrow(results.overall$judge.info.table.combined)) # For everyone
```

# Get the partial orderings

```{r}
# Constructing the rank-based partial order graph
library(dplyr)
library(tidyr)

# Extract the relevant columns
df <- top10_judges %>%
  dplyr::select(Judge_Name, s_j = rank_v2, f_j = rank_fta) %>%
  tidyr::drop_na()


# Initialize empty edge list
edges <- data.frame(from = character(), to = character(), stringsAsFactors = FALSE)

# Compare each ordered pair of judges
for (k in 1:nrow(df)) {
  for (j in 1:nrow(df)) {
    if (k != j) {
      # Apply dominance rule: s_k ≥ s_j and f_k ≤ f_j, with at least one strict inequality
      if ((df$s_j[k] >= df$s_j[j]) &&
          (df$f_j[k] <= df$f_j[j]) &&
          ((df$s_j[k] != df$s_j[j]) || (df$f_j[k] != df$f_j[j]))) {
        edges <- rbind(edges, data.frame(from = df$Judge_Name[k],
                                         to   = df$Judge_Name[j],
                                         stringsAsFactors = FALSE))
      }
    }
  }
}

# Optional: remove transitive edges (to produce a Hasse diagram)
# You can skip this step if you just need the full dominance relation
# library(igraph)
# g <- graph_from_data_frame(edges, vertices = df$Judge_Name, directed = TRUE)
# edges <- as_data_frame(simplify(g, remove.multiple = TRUE, remove.loops = TRUE))

# Return the sets of vertices and edges
vertices <- df$Judge_Name
dominance_graph <- list(vertices = vertices, edges = edges)

# Inspect
dominance_graph$edges

```

N.B.: "from" is who's worse. "to" is who's better. 

# Accounting for uncertainty.

"For all judge A B pairs, if judge A is ranked higher than judge B, how much better does judge B's FTA rate have to be to be equal to that of judge A? how many cases does that tend to be?"

```{r}
library(dplyr)
edges_with_fta_diff <- dominance_graph$edges %>%
  # join "from" judge info (worse judge)
  left_join(
    top10_judges %>%
      select(Judge_Name, pct_fta_from = pct_fta, n_cases_from = n_cases, pct_release_from = pct_release_v2),
    by = c("from" = "Judge_Name")
  ) %>%
  # join "to" judge info (better judge)
  left_join(
    top10_judges %>%
      select(Judge_Name, pct_fta_to = pct_fta),
    by = c("to" = "Judge_Name")
  ) %>%
  mutate(
    # difference in percentage points
    fta_diff = pct_fta_from - pct_fta_to,
    
    # number of released cases for "from" judge
    released_cases_from = n_cases_from * pct_release_from / 100,
    
    # scale by released cases
    fta_diff_cases = (fta_diff / 100) * released_cases_from,
    
    # NEW: percent reduction relative to "from" judge's FTA rate
    fta_diff_relative = fta_diff / pct_fta_from # pct_fta_to? 
  )

edges_with_fta_diff %>% head()

# -----------------------------
# Density plots
# -----------------------------

# 1. Percentage-point differences
d1 <- density(edges_with_fta_diff$fta_diff, na.rm = TRUE)

plot(
  d1,
  main = "Required Reduction in FTA Rate to Offset Rank Differences",
  xlab = "FTA Reduction (percentage points)",
  ylab = "Density"
)

abline(v = mean(edges_with_fta_diff$fta_diff, na.rm = TRUE), lty = 2)
abline(v = median(edges_with_fta_diff$fta_diff, na.rm = TRUE), lty = 3)

legend(
  "topright",
  legend = c("Mean", "Median"),
  lty = c(2, 3),
  bty = "n"
)

# 2. Case differences
d2 <- density(edges_with_fta_diff$fta_diff_cases, na.rm = TRUE)

plot(
  d2,
  main = "Equivalent Reduction in FTA Cases Among Released Defendants",
  xlab = "Reduction in Number of FTA Cases",
  ylab = "Density"
)

abline(v = mean(edges_with_fta_diff$fta_diff_cases, na.rm = TRUE), lty = 2)
abline(v = median(edges_with_fta_diff$fta_diff_cases, na.rm = TRUE), lty = 3)

legend(
  "topright",
  legend = c("Mean", "Median"),
  lty = c(2, 3),
  bty = "n"
)

# 3. Relative reduction (fraction of "from" judge FTA rate)
d3 <- density(edges_with_fta_diff$fta_diff_relative, na.rm = TRUE)

plot(
  d3,
  main = "Required Reduction as Fraction of Baseline FTA Rate",
  xlab = "Fraction of From-Judge FTA Rate",
  ylab = "Density"
)

abline(v = mean(edges_with_fta_diff$fta_diff_relative, na.rm = TRUE), lty = 2)
abline(v = median(edges_with_fta_diff$fta_diff_relative, na.rm = TRUE), lty = 3)

legend(
  "topright",
  legend = c("Mean", "Median"),
  lty = c(2, 3),
  bty = "n"
)

# -----------------------------
# Summary statistics
# -----------------------------

summary_stats <- edges_with_fta_diff %>%
  summarise(
    # percentage-point differences
    mean_fta_diff   = mean(fta_diff, na.rm = TRUE),
    median_fta_diff = median(fta_diff, na.rm = TRUE),
    iqr_fta_diff    = IQR(fta_diff, na.rm = TRUE),
    
    # case differences
    mean_fta_cases   = mean(fta_diff_cases, na.rm = TRUE),
    median_fta_cases = median(fta_diff_cases, na.rm = TRUE),
    iqr_fta_cases    = IQR(fta_diff_cases, na.rm = TRUE),
    
    # relative reduction
    mean_fta_relative   = mean(fta_diff_relative, na.rm = TRUE),
    median_fta_relative = median(fta_diff_relative, na.rm = TRUE),
    iqr_fta_relative    = IQR(fta_diff_relative, na.rm = TRUE)
  )

summary_stats
```


# Stability Analysis for Partial Ordering 

```{r}
set.seed(02138)

check_edge_simulation <- function(edge_row, sim_list) {
  
  from_judge <- edge_row$from
  to_judge   <- edge_row$to
  
  from_mat <- sim_list[[from_judge]]
  to_mat   <- sim_list[[to_judge]]
  
  # ensure same number of simulations
  B <- min(nrow(from_mat), nrow(to_mat))
  
  from_mat <- from_mat[1:B, ]
  to_mat   <- to_mat[1:B, ]
  
  # relation:
  # stricter = lower release rate
  stricter_relation <- from_mat$release_rate_sim < to_mat$release_rate_sim
  
  # worse FTA = higher FTA
  worse_fta_relation <- from_mat$fta_rate_sim > to_mat$fta_rate_sim
  
  relation_holds <- stricter_relation & worse_fta_relation
  
  tibble::tibble(
    from = from_judge,
    to = to_judge,
    pct_relation_holds = mean(relation_holds, na.rm = TRUE) * 100,
    n_holds = sum(relation_holds, na.rm = TRUE),
    B = B
  )
}

start_time <- Sys.time()
# edge_support_sim %>% head()


# Run the simulation
edge_support_sim <- lapply(seq_len(nrow(edges)), function(i) {
  check_edge_simulation(edges[i, ], sim_list)
}) %>%
  dplyr::bind_rows()

# save(edge_support_sim, file = "[2026.03.24] edge_support_sim.RData")
# load("[2026.03.24] edge_support_sim.RData.RData")

end_time <- Sys.time()


runtime <- end_time - start_time
print(runtime)

library(dplyr)

edges <- edge_support_sim %>%
  filter(pct_relation_holds > 60) %>%
  select(from, to)

```


# Longest chains and anti chains

```{r}
library(igraph)

# g <- graph_from_data_frame(
#   dominance_graph$edges, # original setup
#                            vertices = dominance_graph$vertices,
#                            directed = TRUE)

# --- get unique nodes from filtered edges ---
vertex_names <- unique(c(edges$from, edges$to))

# --- build graph ---
g <- graph_from_data_frame(
  edges,
  vertices = vertex_names,   # works if vertices is just a character vector
  directed = TRUE
)


# assumes DAG (dominance should be acyclic); if not, stop
stopifnot(is_dag(g))

topo <- topo_sort(g, mode = "out")
dp   <- rep(1L, vcount(g))     # best path length starting at v
nxt  <- rep(NA_integer_, vcount(g))  # next vertex on that best path

# process in reverse topological order
for (v in rev(topo)) {
  outs <- neighbors(g, v, mode = "out")
  if (length(outs) == 0) next
  best <- outs[ which.max(dp[outs]) ]
  dp[v]  <- 1L + dp[best]
  nxt[v] <- best
}

start <- which.max(dp)

# reconstruct chain
chain_idx <- integer()
cur <- start
while (!is.na(cur)) {
  chain_idx <- c(chain_idx, cur)
  cur <- nxt[cur]
}

longest_chain <- V(g)$name[chain_idx]
longest_chain
length(longest_chain)          # number of vertices in chain
length(longest_chain) - 1L     # number of edges in chain

# Antichatin
library(igraph)

# Step 1: make an undirected comparability graph
g_comp <- as.undirected(g, mode = "collapse")

# Step 2: remove self-loops if any
g_comp <- simplify(g_comp, remove.multiple = TRUE, remove.loops = TRUE)

# Step 3: build the incomparability graph
g_incomp <- complementer(g_comp, loops = FALSE)

# Step 4: get all largest cliques = all maximum antichains
largest_antichains_idx <- largest_cliques(g_incomp)

# Convert first one to judge names
longest_antichain <- V(g_incomp)$name[largest_antichains_idx[[1]]]

# Output
longest_antichain
length(longest_antichain)
```


# graph with data - Figure 1


```{r}
# Filter to only those edges containing the top 5 most prolific judges 
## Store existing object just in case
edges.prime <- edges
top5_judges <- judge.info.table.combined %>%
  arrange(desc(n_cases)) %>%
  slice(1:5) %>% # Adjust this for graph specs. A.9
  pull(Judge_Name)

edges <- edges %>%
  filter(from %in% top5_judges & to %in% top5_judges)

# partial.ordering
library(igraph)

# --- get unique nodes from filtered edges ---
vertex_names <- unique(c(edges$from, edges$to))

# --- build graph ---
g <- graph_from_data_frame(
  edges,
  vertices = data.frame(name = top5_judges),  # <- key fix
  directed = TRUE
)

short_labels <- sub(",.*$", "", V(g)$name)

# Sugiyama layout
lay <- layout_with_sugiyama(g)$layout

# Rotate layout so ordering goes left → right
lay <- cbind(lay[,2], lay[,1])

# spacing
horizontal_spacing <- 40
vertical_spacing   <- 16

lay[,1] <- lay[,1] * horizontal_spacing
lay[,2] <- lay[,2] * vertical_spacing

# label direction
deg <- ifelse(lay[,1] < median(lay[,1]), pi, 0)

png(
  filename = "[2026.04.25] Partial Ordering top 10.png",
  width = 60,
  height = 30,
  units = "in",
  res = 300,
  bg = "white"
)

plot(
  g,
  layout = lay,
  vertex.size = 10,
  vertex.color = "skyblue",
  vertex.frame.color = "gray40",
  vertex.label = short_labels,
  vertex.label.cex = 2.5,
  vertex.label.dist = 0,
  vertex.label.degree = deg,
  edge.arrow.size = 0.6,
  edge.color = "gray40",
  cex.main = 2.5,   # <-- THIS controls title size,
  col.main = "white"

)

dev.off()
```

# Descriptive Statistics - Table 2

## Decisions at arraignment (Make categories)

```{r}
# set to filtered data
data <- data.prelim

# If focusing on qualifying offenses: 
data$release_v1 <- data$release_v2

# -------------------------------
# Define eligibility (i.e., valid arraignment decisions)
# -------------------------------
eligible_idx <- which(!is.na(data$release_v1))

# -------------------------------
# Define release vs detain based on v1
# -------------------------------
release_idx <- which(data$release_v1 == 1)
detain_idx  <- which(data$release_v1 == 0)

# (Optional sanity check: ensure both are subsets of eligible)
release_idx <- intersect(release_idx, eligible_idx)
detain_idx  <- intersect(detain_idx,  eligible_idx)

# -------------------------------
# Create datasets
# -------------------------------
data_release <- data[release_idx, ]
data_detain  <- data[detain_idx,  ]

# -------------------------------
# (Optional) explicitly track excluded cases
# -------------------------------
exclude_idx <- which(is.na(data$release_v1))
data_excluded <- data[exclude_idx, ]

```


## What percentage were released on recognizance? 

```{r}
# For the 'release' group
pct_ror_release <- mean(data_release$ROR_at_Arraign == "Y", na.rm = TRUE) * 100

# For the 'detain' group
pct_ror_detain <- mean(data_detain$ROR_at_Arraign == "Y", na.rm = TRUE) * 100

cat("Percentage ROR in release group:", round(pct_ror_release, 2), "%\n")
cat("Percentage ROR in detain group:", round(pct_ror_detain, 2), "%\n")

```

## What percentage had monetary bail

```{r}
# For the 'release' group
pct_bail_set_release <- mean(
  data_release$Bail_Set_and_Posted_at_Arraign == "Y" |
  data_release$Bail_Set_and_Not_Posted_at_Arraign == "Y",
  na.rm = TRUE
) * 100

# For the 'detain' group
pct_bail_set_detain <- mean(
  data_detain$Bail_Set_and_Posted_at_Arraign == "Y" |
  data_detain$Bail_Set_and_Not_Posted_at_Arraign == "Y",
  na.rm = TRUE
) * 100

cat("Percentage with bail set (release group):", round(pct_bail_set_release, 2), "%\n")
cat("Percentage with bail set (detain group):", round(pct_bail_set_detain, 2), "%\n")

```

## Monitoring conditions. 

```{r}
# Top 3 most common electronic monitoring conditions in the dataset
# Select the relevant columns
cols <- data[, 49:62]

# Count number of "Y"s per column
y_counts <- sapply(cols, function(col) sum(col == "Y", na.rm = TRUE))

# Sort and get the top 3
top3 <- sort(y_counts, decreasing = TRUE)[1:5]

print(top3)

```
## Monitoring conditions breakdown. 

```{r}
# Define a helper function for the calculation
get_pct_Y <- function(df) {
  # New column: Y if either supervision or contact is Y
  supervision_or_agency <- (df$Pretrial_Supervision_at_Arraign == "Y" | 
                            df$Contact_Pretrial_Service_Agency == "Y")
  pct_supervision_or_agency <- mean(supervision_or_agency, na.rm = TRUE) * 100
  
  pct_other_nmr <- mean(df$Other_NMR == "Y", na.rm = TRUE) * 100
  pct_electronic_monitoring <- mean(df$Electronic_Monitoring == "Y", na.rm = TRUE) * 100
  pct_no_firearms <- mean(df$No_Firearms_or_Weapons == "Y", na.rm = TRUE) * 100
  
  return(
    c(
      pct_supervision_or_agency = round(pct_supervision_or_agency, 2),
      pct_other_nmr = round(pct_other_nmr, 2),
      pct_electronic_monitoring = round(pct_electronic_monitoring, 2),
      pct_no_firearms = round(pct_no_firearms, 2)
    )
  )
}

# Apply to each group
release_supervision <- get_pct_Y(data_release)
detain_supervision  <- get_pct_Y(data_detain)

cat("Release group:\n")
print(release_supervision)
cat("\nDetain group:\n")
print(detain_supervision)

```
## Nonmonetary bail

```{r}
# Helper function for percentage of NMR == "Y"
get_pct_nmr <- function(df) {
  mean(df$NMR_at_Arraign == "Y", na.rm = TRUE) * 100
}

# Apply to release and detain groups
release_nmr <- get_pct_nmr(data_release)
detain_nmr  <- get_pct_nmr(data_detain)

cat("Release group:\n")
print(round(release_nmr, 2))
cat("\nDetain group:\n")
print(round(detain_nmr, 2))

```

## demographic info:

```{r}
# race age
data %>%
  summarize(
    pct_male = mean(Gender == "Male", na.rm = TRUE) * 100,
    pct_nonwhite = mean(!(Race %in% c("White", "Unknown")) & !is.na(Race), na.rm = TRUE) * 100,
    pct_hispanic = mean(Ethnicity == "Hispanic", na.rm = TRUE) * 100
    # ,
    # median_age = median(Age_at_Arrest, na.rm = TRUE),
    # p25_age = quantile(Age_at_Arrest, 0.25, na.rm = TRUE),
    # p75_age = quantile(Age_at_Arrest, 0.75, na.rm = TRUE)
  )

# Priors

# Helper function to calculate the percentage where any of the variables > 0
pct_any_prior_or_pending <- function(df) {
  mean(
    df$prior_vfo_cnt    > 0 |
    df$prior_nonvfo_cnt > 0 |
    df$prior_misd_cnt   > 0, # |
    # df$pend_vfo         > 0 |
    # df$pend_nonvfo      > 0 |
    # df$pend_misd        > 0,
    na.rm = TRUE
  ) * 100
}

# Apply to both datasets
pct_prior_pending_release <- pct_any_prior_or_pending(data_release)
pct_prior_pending_detain  <- pct_any_prior_or_pending(data_detain)

cat("Percentage with any prior/pending (release group):", round(pct_prior_pending_release, 2), "%\n")
cat("Percentage with any prior/pending (detain group):", round(pct_prior_pending_detain, 2), "%\n")

## Redone

get_demographic_stats <- function(df) {
  list(
    pct_male     = mean(df$Gender == "Male", na.rm = TRUE) * 100,
    pct_nonwhite = mean(!(df$Race %in% c("White", "Unknown")) & !is.na(df$Race), na.rm = TRUE) * 100,
    pct_hispanic = mean(df$Ethnicity == "Hispanic", na.rm = TRUE) * 100,
    # median_age   = median(df$Age_at_Arrest, na.rm = TRUE),
    # p25_age      = quantile(df$Age_at_Arrest, 0.25, na.rm = TRUE),
    # p75_age      = quantile(df$Age_at_Arrest, 0.75, na.rm = TRUE),
    pct_any_prior = mean(
      df$prior_vfo_cnt    > 0 |
      df$prior_nonvfo_cnt > 0 |
      df$prior_misd_cnt   > 0,
      na.rm = TRUE
    ) * 100
  )
}

release_demo <- get_demographic_stats(data_release)
detain_demo  <- get_demographic_stats(data_detain)

cat("Release group:\n")
print(release_demo)
cat("\nDetain group:\n")
print(detain_demo)


```


## representation

```{r}
# Helper function to get %Y and %N, excluding N/A
get_pct_representation <- function(df) {
  valid <- df %>%
    filter(Representation_at_Securing_Order %in% c("Y", "N"))
  
  pct_yes <- mean(valid$Representation_at_Securing_Order == "Y", na.rm = TRUE) * 100
  pct_no  <- mean(valid$Representation_at_Securing_Order == "N", na.rm = TRUE) * 100
  
  return(c(pct_yes = round(pct_yes, 2), pct_no = round(pct_no, 2)))
}

# Apply to release and detain groups
release_representation <- get_pct_representation(data_release)
detain_representation  <- get_pct_representation(data_detain)

cat("Release group:\n")
print(release_representation)

cat("\nDetain group:\n")
print(detain_representation)

```


## Outcomes

```{r eval=FALSE, include=FALSE}
# Define imprisonment-related values
imprisonment_vals <- c("Imprisonment", "Imprisonment Time Served", "Imprisonment-Not Time Served")

get_outcome_percentages_with_imprisonment <- function(df) {
  pct_plea <- mean(df$Disposition_Type == "Plea", na.rm = TRUE) * 100
  pct_rearrest <- mean(!(df$rearrest %in% c("NULL", "No Arrest")) & !is.na(df$rearrest), na.rm = TRUE) * 100
  pct_verdict_tfg <- mean(df$Disposition_Type == "Verdict-TFG", na.rm = TRUE) * 100
  pct_imprisonment <- mean(df$Most_Severe_Sentence %in% imprisonment_vals, na.rm = TRUE) * 100
  
  return(
    c(
      pct_plea = round(pct_plea, 2),
      pct_rearrest = round(pct_rearrest, 2),
      pct_verdict_tfg = round(pct_verdict_tfg, 2),
      pct_imprisonment = round(pct_imprisonment, 2)
    )
  )
}

# Apply to both datasets
release_outcomes <- get_outcome_percentages_with_imprisonment(data_release)
detain_outcomes  <- get_outcome_percentages_with_imprisonment(data_detain)

cat("Release group:\n")
print(release_outcomes)
cat("\nDetain group:\n")
print(detain_outcomes)

# For the release group
subset_release <- data_release$Release.Decision.at.Arraign != "Disposed at arraign" &
                  !is.na(data_release$Release.Decision.at.Arraign)

fta_release <- mean(data_release$Warrant_Ordered_btw_Arraign_and_Dispo[subset_release] == "Y", na.rm = TRUE) * 100

# For the detain group
subset_detain <- data_detain$Release.Decision.at.Arraign != "Disposed at arraign" &
                 !is.na(data_detain$Release.Decision.at.Arraign)

fta_detain <- mean(data_detain$Warrant_Ordered_btw_Arraign_and_Dispo[subset_detain] == "Y", na.rm = TRUE) * 100

cat("FTA percentage (release group):", round(fta_release, 2), "%\n")
cat("FTA percentage (detain group):", round(fta_detain, 2), "%\n")

```

## How many judges in each group

```{r}
n_judges_release <- n_distinct(data_release$Judge_Name)
n_judges_detain  <- n_distinct(data_detain$Judge_Name)

cat("Number of distinct judges (release group):", n_judges_release, "\n")
cat("Number of distinct judges (detain group):", n_judges_detain, "\n")
```

## Number of observations

```{r}
data_release %>% nrow()

data_detain %>% nrow()
```
## Number of cases a judge hears in each group

```{r}
# For data_release
data_release %>%
  count(Judge_Name) %>%
  summarize(
    n_judges = n(),                    # number of unique judges
    median_cases = median(n),          # median number of cases per judge
    p25_cases = quantile(n, 0.25),     # 25th percentile
    p75_cases = quantile(n, 0.75)      # 75th percentile
  )

# For data_detain
data_detain %>%
  count(Judge_Name) %>%
  summarize(
    n_judges = n(),                    # number of unique judges
    median_cases = median(n),          # median number of cases per judge
    p25_cases = quantile(n, 0.25),     # 25th percentile
    p75_cases = quantile(n, 0.75)      # 75th percentile
  )

```

# Get Qualifying Charges. 

## June 2023

```{r}
# First clear environment and reload the preliminaries. 

# Clear environment
rm(list = ls())

library(dplyr)
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(sandwich)
library(readr)
library(lmtest)

# Create data.prelim object first.
# Load the data 

data.2020 <- read.csv("data.ny.2020.csv")
data.2021    <- read.csv("data.ny.2021.csv")
data.2022   <- read.csv("data.ny.2022.csv")
data.2023       <- read.csv("data.ny.2023.csv")
data.2024   <- read.csv("data.ny.2024.csv")
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2021 <- read_csv(
#   "data.ny.2021.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2022 <- read_csv(
#   "data.ny.2022.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2023 <- read_csv(
#   "data.ny.2023.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2024 <- read_csv(
#   "data.ny.2024.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )

# Combine the data 
data <- rbind(data.2020, data.2021, data.2022, data.2023, data.2024)


# # Debugging
# library(readr)
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# nrow(data.2020)
# problems(data.2020)



# Create the different varibles.

# failure to appear
w <- toupper(trimws(data$Warrant_Ordered_btw_Arraign_and_Dispo))
d <- data$Release.Decision.at.Arraign == "Disposed at arraign"
data$fta_flag <- ifelse(d, NA_real_, ifelse(w == "Y", 1, ifelse(w == "N", 0, NA_real_)))

# release decisions
data <- data %>%
  mutate(release_v1 = ifelse(
    Release.Decision.at.Arraign == "ROR" | Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v1: defendant considered release iff they are released unconditionally.

data <- data %>%
  mutate(release_v2 = ifelse(
    Release.Decision.at.Arraign %in% c("ROR", "Nonmonetary release") | # more lenient
      Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v2: defendant considered release iff they are released with or without conditions.

# Force NA when disposed at arraignment or unknown
data <- data %>%
  mutate(
    release_v1 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v1),
    release_v2 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v2)
  )

# Force FTA to NA when defendant was not released under release_v2 - COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
data <- data %>%
  mutate(
    fta_flag = ifelse(release_v2 == 0, NA_real_, fta_flag)
  )

# Set new data object
data.prelim <- data


# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail


##### 

# Function containing strings
contains_any <- function(x, patterns) {
  # x: single string (e.g., one charge)
  # patterns: character vector of strings to search for
  
  pattern_regex <- paste(patterns, collapse = "|")
  grepl(pattern_regex, x)
}

# example usage
patterns <- c("215.50", "215.50")
contains_any(
  "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt",
  patterns
)

# debugging to see if the strings are in there. 
my_string <- "AF"
any(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
mean(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
data.prelim$Top_Charge_at_Arraign[
  grepl(my_string, data.prelim$Top_Charge_at_Arraign)
] %>% unique

# Generate string for qualifying offenses. 
qualifying.offenses.charge.2023.06.09 <- c("70.02", # (a)
                                           "215.15", # (b)
                                           "215.11", "215.12", "215.13", # (c)
                                           # mechanism for identifying (d) can be found below
                                           "230.34", "70.80", "255.25", "255.26", "255.27", "130", # (e)
                                           "105.15", # (f)
                                           "470.24", "470.23", "470.22", "470.21", "490", # (g)
                                           "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt", "PL 110-215.50 03 BM Crim Contempt-2nd:Disobey Crt", "PL 215.51 C EF Crim Cont-1: Pl215.50(3)-Prior", # (h)
                                           "263.30", "263.05", "120.70", "263.10", "263.15", # (i)
                                           "125", # (j)
                                           "121.11", "121.12", "135.10", # (k)
                                           "120.04", # (l)
                                           # mechanism for identifying (m) can be found below
                                           "120.12", "PL 265.01-A EF Crim Poss Weapon School Grds", # (n)
                                           "155.42", "460.20", "470.20", # (o)
                                           "168", "260.10", # (p)
                                           "215.55", "215.56", "215.57", "205.05", "205.10", "205.15", # (q)
                                           # mechanism for identifying (r) can be found below
                                           "70.10", # (s)
                                           # (t) is TBD
                                           "265.02 03", "265.16" # (u)
                                           )

# For subsection d of 2023.06.09. 
qualifying.offenses.charge.weight.2023.06.09 <- "AF"

# For subsection m of 2023.06.09.
hate_assault3.2023.06.09 <- function(x) {
  if ((grepl("120\\.00", x) & grepl("Hate", x)) |
      (grepl("150\\.10", x) & grepl("Hate", x))) {
    return(1)
  } else {
    return(0)
  }
}

# For subsection r of 2023.06.09.
felony_supervision.2023.06.09 <- function(x) {
  if (x[1] == "Felony" & x[2] == 1) {
    return(1)
  } else {
    return(0)
  }
}

# Create the function to determine if the offense qualifies under 2023.06.09 version. 
qualifyng.charges.2023.06.09.function <- function(index = 1, data = data.prelim, date = "2023-06-01"){
  # Check the arraignment date for this row
  arraign_date <- as.Date(data$First_Arraign_Date[index], "%m/%d/%Y")

  if (is.na(arraign_date) || arraign_date < as.Date(date)) {
    return(0)
  }
  
  # Sections (a) through (u) excluding (d), (m), and (r)
  result1 <- contains_any(x = data$Top_Charge_at_Arraign[index], patterns = qualifying.offenses.charge.2023.06.09) %>% as.numeric()
  
  # (d)
  result2 <- data$Top_Charge_Weight_at_Arraign[index] == qualifying.offenses.charge.weight.2023.06.09
  result2 <- result2 %>% as.numeric()
  
  # (m)
  result3 <- data$Top_Charge_at_Arraign[index] %>% hate_assault3.2023.06.09() %>% as.numeric()
  
  # (r)
  result4 <- data[index, c("Top_Severity_at_Arraign", "supervision")] %>% felony_supervision.2023.06.09() %>% as.numeric()
  
  # Double checking section references
  result5 <- contains_any(x = data$Top_Arraign_Article_Section[index], patterns = qualifying.offenses.charge.2023.06.09) %>% as.numeric()
  
  # Tally all conditions
  result <- result1 + result2 + result3 + result4 + result5
  
  # Are any of the conditions satisfied? They are if the sum is greater than zero.
  result <- result > 0
  
  # Conver result to number and return
  result <- result %>% as.numeric()
  result %>% return()
}

# Run the function and get vector indicating whether the charge qualifies under the 2023.06.09 changes post facto. 
qualifyng.charges.2023.06.09.indicator <- sapply(X = 1:nrow(data.prelim), FUN = qualifyng.charges.2023.06.09.function)

save(qualifyng.charges.2023.06.09.indicator,     file = "[2026.05.02] qualifyng.charges.2023.06.09.indicator.RData")
```

## May 2022

```{r}
# Clear environment
rm(list = ls())

library(dplyr)
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(sandwich)
library(readr)
library(lmtest)

# Create data.prelim object first.
# Load the data 

data.2020 <- read.csv("data.ny.2020.csv")
data.2021    <- read.csv("data.ny.2021.csv")
data.2022   <- read.csv("data.ny.2022.csv")
data.2023       <- read.csv("data.ny.2023.csv")
data.2024   <- read.csv("data.ny.2024.csv")
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2021 <- read_csv(
#   "data.ny.2021.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2022 <- read_csv(
#   "data.ny.2022.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2023 <- read_csv(
#   "data.ny.2023.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2024 <- read_csv(
#   "data.ny.2024.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )

# Combine the data 
data <- rbind(data.2020, data.2021, data.2022, data.2023, data.2024)


# # Debugging
# library(readr)
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# nrow(data.2020)
# problems(data.2020)



# Create the different varibles.

# failure to appear
w <- toupper(trimws(data$Warrant_Ordered_btw_Arraign_and_Dispo))
d <- data$Release.Decision.at.Arraign == "Disposed at arraign"
data$fta_flag <- ifelse(d, NA_real_, ifelse(w == "Y", 1, ifelse(w == "N", 0, NA_real_)))

# release decisions
data <- data %>%
  mutate(release_v1 = ifelse(
    Release.Decision.at.Arraign == "ROR" | Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v1: defendant considered release iff they are released unconditionally.

data <- data %>%
  mutate(release_v2 = ifelse(
    Release.Decision.at.Arraign %in% c("ROR", "Nonmonetary release") | # more lenient
      Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v2: defendant considered release iff they are released with or without conditions.

# Force NA when disposed at arraignment or unknown
data <- data %>%
  mutate(
    release_v1 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v1),
    release_v2 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v2)
  )

# Force FTA to NA when defendant was not released under release_v2 - COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
data <- data %>%
  mutate(
    fta_flag = ifelse(release_v2 == 0, NA_real_, fta_flag)
  )

# Set new data object
data.prelim <- data


# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail


##### 

# Function containing strings
contains_any <- function(x, patterns) {
  # x: single string (e.g., one charge)
  # patterns: character vector of strings to search for
  
  pattern_regex <- paste(patterns, collapse = "|")
  grepl(pattern_regex, x)
}

# example usage
patterns <- c("215.50", "215.50")
contains_any(
  "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt",
  patterns
)

# debugging to see if the strings are in there. 
my_string <- "AF"
any(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
mean(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
data.prelim$Top_Charge_at_Arraign[
  grepl(my_string, data.prelim$Top_Charge_at_Arraign)
] %>% unique

# Generate string for qualifying offenses. 
qualifying.offenses.charge.2022.05.01 <- c("70.02", # (a)
                                           "215.15", # (b)
                                           "215.11", "215.12", "215.13", # (c)
                                           # mechanism for identifying (d) can be found below
                                           "230.34", "70.80", "255.25", "255.26", "255.27", "130", # (e)
                                           "105.15", # (f)
                                           "470.24", "470.23", "470.22", "470.21", "490", # (g)
                                           "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt", "PL 110-215.50 03 BM Crim Contempt-2nd:Disobey Crt", "PL 215.51 C EF Crim Cont-1: Pl215.50(3)-Prior", # (h)
                                           "263.30", "263.05", "120.70", "263.10", "263.15", # (i)
                                           "125", # (j)
                                           "121.11", "121.12", "135.10", # (k)
                                           "120.04", # (l)
                                           # mechanism for identifying (m) can be found below
                                           "120.12", "PL 265.01-A EF Crim Poss Weapon School Grds", # (n)
                                           "155.42", "460.20", "470.20", # (o)
                                           "168", "260.10", # (p)
                                           "215.55", "215.56", "215.57", "205.05", "205.10", "205.15", # (q)
                                           # mechanism for identifying (r) can be found below
                                           "70.10", # (s)
                                           # (t) is TBD
                                           "265.02 03", "265.16" # (u)
                                           )

# For subsection d of 2022.05.01. 
qualifying.offenses.charge.weight.2022.05.01 <- "AF"

# For subsection m of 2022.05.01.
hate_assault3.2022.05.01 <- function(x) {
  if ((grepl("120\\.00", x) & grepl("Hate", x)) |
      (grepl("150\\.10", x) & grepl("Hate", x))) {
    return(1)
  } else {
    return(0)
  }
}

# For subsection r of 2022.05.01.
felony_supervision.2022.05.01 <- function(x) {
  if (x[1] == "Felony" & x[2] == 1) {
    return(1)
  } else {
    return(0)
  }
}

# Create the function to determine if the offense qualifies under 2022.05.01 version. 
qualifyng.charges.2022.05.01.function <- function(index = 1, data = data.prelim, date = "2022-05-01"){
  # Check the arraignment date for this row
  arraign_date <- as.Date(data$First_Arraign_Date[index], "%m/%d/%Y")

  if (is.na(arraign_date) || arraign_date < as.Date(date)) {
    return(0)
  }
  
  # Sections (a) through (u) excluding (d), (m), and (r)
  result1 <- contains_any(x = data$Top_Charge_at_Arraign[index], patterns = qualifying.offenses.charge.2022.05.01) %>% as.numeric()
  
  # (d)
  result2 <- data$Top_Charge_Weight_at_Arraign[index] == qualifying.offenses.charge.weight.2022.05.01
  result2 <- result2 %>% as.numeric()
  
  # (m)
  result3 <- data$Top_Charge_at_Arraign[index] %>% hate_assault3.2022.05.01() %>% as.numeric()
  
  # (r)
  result4 <- data[index, c("Top_Severity_at_Arraign", "supervision")] %>% felony_supervision.2022.05.01() %>% as.numeric()
  
  # Double checking section references
  result5 <- contains_any(x = data$Top_Arraign_Article_Section[index], patterns = qualifying.offenses.charge.2022.05.01) %>% as.numeric()
  
  # Tally all conditions
  result <- result1 + result2 + result3 + result4 + result5
  
  # Are any of the conditions satisfied? They are if the sum is greater than zero.
  result <- result > 0
  
  # Conver result to number and return
  result <- result %>% as.numeric()
  result %>% return()
}

# Run the function and get vector indicating whether the charge qualifies under the 2022.05.01 changes post facto. 
qualifyng.charges.2022.05.01.indicator <- sapply(X = 1:nrow(data.prelim), FUN = qualifyng.charges.2022.05.01.function)

save(qualifyng.charges.2022.05.01.indicator,     file = "[2026.05.02] qualifyng.charges.2022.05.01.indicator.RData")

```


## July 2020


```{r}

# Clear environment
rm(list = ls())

library(dplyr)
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(sandwich)
library(readr)
library(lmtest)

# Create data.prelim object first.
# Load the data 

data.2020 <- read.csv("data.ny.2020.csv")
data.2021    <- read.csv("data.ny.2021.csv")
data.2022   <- read.csv("data.ny.2022.csv")
data.2023       <- read.csv("data.ny.2023.csv")
data.2024   <- read.csv("data.ny.2024.csv")
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2021 <- read_csv(
#   "data.ny.2021.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2022 <- read_csv(
#   "data.ny.2022.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2023 <- read_csv(
#   "data.ny.2023.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2024 <- read_csv(
#   "data.ny.2024.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )

# Combine the data 
data <- rbind(data.2020, data.2021, data.2022, data.2023, data.2024)


# # Debugging
# library(readr)
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# nrow(data.2020)
# problems(data.2020)



# Create the different varibles.

# failure to appear
w <- toupper(trimws(data$Warrant_Ordered_btw_Arraign_and_Dispo))
d <- data$Release.Decision.at.Arraign == "Disposed at arraign"
data$fta_flag <- ifelse(d, NA_real_, ifelse(w == "Y", 1, ifelse(w == "N", 0, NA_real_)))

# release decisions
data <- data %>%
  mutate(release_v1 = ifelse(
    Release.Decision.at.Arraign == "ROR" | Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v1: defendant considered release iff they are released unconditionally.

data <- data %>%
  mutate(release_v2 = ifelse(
    Release.Decision.at.Arraign %in% c("ROR", "Nonmonetary release") | # more lenient
      Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v2: defendant considered release iff they are released with or without conditions.

# Force NA when disposed at arraignment or unknown
data <- data %>%
  mutate(
    release_v1 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v1),
    release_v2 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v2)
  )

# Force FTA to NA when defendant was not released under release_v2 - COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
data <- data %>%
  mutate(
    fta_flag = ifelse(release_v2 == 0, NA_real_, fta_flag)
  )

# Set new data object
data.prelim <- data


# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail


#####

# Function containing strings
contains_any <- function(x, patterns) {
  # x: single string (e.g., one charge)
  # patterns: character vector of strings to search for
  
  pattern_regex <- paste(patterns, collapse = "|")
  grepl(pattern_regex, x)
}

# example usage
patterns <- c("215.50", "215.50")
contains_any(
  "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt",
  patterns
)

# # debugging to see if the strings are in there. 
# my_string <- "AF"
# any(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
# mean(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
# data.prelim$Top_Charge_at_Arraign[
#   grepl(my_string, data.prelim$Top_Charge_at_Arraign)
# ] %>% unique

# Generate string for qualifying offenses. 
qualifying.offenses.charge.2020.07.01 <- c("70.02", # (a)
                                           "215.15", # (b)
                                           "215.11", "215.12", "215.13", # (c)
                                           # mechanism for identifying (d) can be found below
                                           "230.34", "70.80", "255.25", "255.26", "255.27", "130", # (e)
                                           "105.15", # (f)
                                           "470.24", "470.23", "470.22", "470.21", "490", # (g)
                                           "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt", "PL 110-215.50 03 BM Crim Contempt-2nd:Disobey Crt", "PL 215.51 C EF Crim Cont-1: Pl215.50(3)-Prior", # (h)
                                           "263.30", "263.05", "120.70", "263.10", "263.15", # (i)
                                           "125", # (j)
                                           "121.11", "121.12", "135.10", # (k)
                                           "120.04", # (l)
                                           # mechanism for identifying (m) can be found below
                                           "120.12", "PL 265.01-A EF Crim Poss Weapon School Grds", # (n)
                                           "155.42", "460.20", "470.20", # (o)
                                           "168", "260.10", # (p)
                                           "215.55", "215.56", "215.57", "205.05", "205.10", "205.15", # (q)
                                           # mechanism for identifying (r) can be found below
                                           "70.10"
                                           # , # (s)
                                           # (t) is TBD
                                           )

# For subsection d of 2020.07.01. 
qualifying.offenses.charge.weight.2020.07.01 <- "AF"

# For subsection m of 2020.07.01.
hate_assault3.2020.07.01 <- function(x) {
  if ((grepl("120\\.00", x) & grepl("Hate", x)) |
      (grepl("150\\.10", x) & grepl("Hate", x))) {
    return(1)
  } else {
    return(0)
  }
}

# For subsection r of 2020.07.01.
felony_supervision.2020.07.01 <- function(x) {
  if (x[1] == "Felony" & x[2] == 1) {
    return(1)
  } else {
    return(0)
  }
}

# Create the function to determine if the offense qualifies under 2020.07.01 version. 
qualifyng.charges.2020.07.01.function <- function(index = 1, data = data.prelim, date = "2020-07-01"){
  # Check the arraignment date for this row
  arraign_date <- as.Date(data$First_Arraign_Date[index], "%m/%d/%Y")

  if (is.na(arraign_date) || arraign_date < as.Date(date)) {
    return(0)
  }
  
  # Sections (a) through (u) excluding (d), (m), and (r)
  result1 <- contains_any(x = data$Top_Charge_at_Arraign[index], patterns = qualifying.offenses.charge.2020.07.01) %>% as.numeric()
  
  # (d)
  result2 <- data$Top_Charge_Weight_at_Arraign[index] == qualifying.offenses.charge.weight.2020.07.01
  result2 <- result2 %>% as.numeric()
  
  # (m)
  result3 <- data$Top_Charge_at_Arraign[index] %>% hate_assault3.2020.07.01() %>% as.numeric()
  
  # (r)
  result4 <- data[index, c("Top_Severity_at_Arraign", "supervision")] %>% felony_supervision.2020.07.01() %>% as.numeric()
  
  # Double checking section references
  result5 <- contains_any(x = data$Top_Arraign_Article_Section[index], patterns = qualifying.offenses.charge.2020.07.01) %>% as.numeric()
  
  # Tally all conditions
  result <- result1 + result2 + result3 + result4 + result5
  
  # Are any of the conditions satisfied? They are if the sum is greater than zero.
  result <- result > 0
  
  # Conver result to number and return
  result <- result %>% as.numeric()
  result %>% return()
}

# Run the function and get vector indicating whether the charge qualifies under the 2020.07.01 changes post facto. 
qualifyng.charges.2020.07.01.indicator <- sapply(X = 1:nrow(data.prelim), FUN = qualifyng.charges.2020.07.01.function)

save(qualifyng.charges.2020.07.01.indicator,     file = "[2026.05.02] qualifyng.charges.2020.07.01.indicator.RData")

# load("[2026.03.10.1] qualifyng.charges.2020.07.01.indicator.RData")

```


## January 2020

```{r}

# Clear environment
rm(list = ls())

library(dplyr)
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(sandwich)
library(readr)
library(lmtest)

# Create data.prelim object first.
# Load the data 

data.2020 <- read.csv("data.ny.2020.csv")
data.2021    <- read.csv("data.ny.2021.csv")
data.2022   <- read.csv("data.ny.2022.csv")
data.2023       <- read.csv("data.ny.2023.csv")
data.2024   <- read.csv("data.ny.2024.csv")
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2021 <- read_csv(
#   "data.ny.2021.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2022 <- read_csv(
#   "data.ny.2022.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2023 <- read_csv(
#   "data.ny.2023.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2024 <- read_csv(
#   "data.ny.2024.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )

# Combine the data 
data <- rbind(data.2020, data.2021, data.2022, data.2023, data.2024)


# # Debugging
# library(readr)
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# nrow(data.2020)
# problems(data.2020)



# Create the different varibles.

# failure to appear
w <- toupper(trimws(data$Warrant_Ordered_btw_Arraign_and_Dispo))
d <- data$Release.Decision.at.Arraign == "Disposed at arraign"
data$fta_flag <- ifelse(d, NA_real_, ifelse(w == "Y", 1, ifelse(w == "N", 0, NA_real_)))

# release decisions
data <- data %>%
  mutate(release_v1 = ifelse(
    Release.Decision.at.Arraign == "ROR" | Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v1: defendant considered release iff they are released unconditionally.

data <- data %>%
  mutate(release_v2 = ifelse(
    Release.Decision.at.Arraign %in% c("ROR", "Nonmonetary release") | # more lenient
      Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v2: defendant considered release iff they are released with or without conditions.

# Force NA when disposed at arraignment or unknown
data <- data %>%
  mutate(
    release_v1 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v1),
    release_v2 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v2)
  )

# Force FTA to NA when defendant was not released under release_v2 - COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
data <- data %>%
  mutate(
    fta_flag = ifelse(release_v2 == 0, NA_real_, fta_flag)
  )

# Set new data object
data.prelim <- data


# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail


#####

# Function containing strings
contains_any <- function(x, patterns) {
  # x: single string (e.g., one charge)
  # patterns: character vector of strings to search for
  
  pattern_regex <- paste(patterns, collapse = "|")
  grepl(pattern_regex, x)
}

# example usage
patterns <- c("215.50", "215.50")
contains_any(
  "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt",
  patterns
)

# # debugging to see if the strings are in there. 
# my_string <- "AF"
# any(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
# mean(grepl(my_string, data.prelim$Top_Charge_at_Arraign))
# data.prelim$Top_Charge_at_Arraign[
#   grepl(my_string, data.prelim$Top_Charge_at_Arraign)
# ] %>% unique

# Generate string for qualifying offenses. 
qualifying.offenses.charge.2020.01.01 <- c("70.02", # (a)
                                           "215.15", # (b)
                                           "215.11", "215.12", "215.13", # (c)
                                           # mechanism for identifying (d) can be found below
                                           "230.34", "70.80", "255.25", "255.26", "255.27", "130", # (e)
                                           "105.15", # (f)
                                           "470.24", "470.23", "470.22", "470.21", "490", # (g)
                                           "PL 215.50 03 AM Crim Contempt-2nd:Disobey Crt", "PL 110-215.50 03 BM Crim Contempt-2nd:Disobey Crt", "PL 215.51 C EF Crim Cont-1: Pl215.50(3)-Prior", # (h)
                                           "263.30", "263.05", "120.70" # (i) 
                                           # "263.10", "263.15", # (i)
                                           # "125", # (j)
                                           # "121.11", "121.12", "135.10", # (k)
                                           # "120.04", # (l)
                                           # # mechanism for identifying (m) can be found below
                                           # "120.12", "PL 265.01-A EF Crim Poss Weapon School Grds", # (n)
                                           # "155.42", "460.20", "470.20", # (o)
                                           # "168", "260.10", # (p)
                                           # "215.55", "215.56", "215.57", "205.05", "205.10", "205.15", # (q)
                                           # # mechanism for identifying (r) can be found below
                                           # "70.10"
                                           # # , # (s)
                                           # # (t) is TBD
                                           )

# For subsection d of 2020.01.01. 
qualifying.offenses.charge.weight.2020.01.01 <- "AF"

# # For subsection m of 2020.01.01.
# hate_assault3.2020.01.01 <- function(x) {
#   if ((grepl("120\\.00", x) & grepl("Hate", x)) |
#       (grepl("150\\.10", x) & grepl("Hate", x))) {
#     return(1)
#   } else {
#     return(0)
#   }
# }

# # For subsection r of 2020.01.01.
# felony_supervision.2020.01.01 <- function(x) {
#   if (x[1] == "Felony" & x[2] == 1) {
#     return(1)
#   } else {
#     return(0)
#   }
# }

# Create the function to determine if the offense qualifies under 2020.01.01 version. 
qualifyng.charges.2020.01.01.function <- function(index = 1, data = data.prelim, date = "2020-01-01"){
  # Check the arraignment date for this row
  arraign_date <- as.Date(data$First_Arraign_Date[index], "%m/%d/%Y")

  if (is.na(arraign_date) || arraign_date < as.Date(date)) {
    return(0)
  }
  
  # Sections (a) through (u) excluding (d), (m), and (r)
  result1 <- contains_any(x = data$Top_Charge_at_Arraign[index], patterns = qualifying.offenses.charge.2020.01.01) %>% as.numeric()
  
  # (d)
  result2 <- data$Top_Charge_Weight_at_Arraign[index] == qualifying.offenses.charge.weight.2020.01.01
  result2 <- result2 %>% as.numeric()
  
  # (m)
  result3 <- 0
    # data$Top_Charge_at_Arraign[index] %>% hate_assault3.2020.01.01() %>% as.numeric()
  
  # (r)
  result4 <- 0
    # data[index, c("Top_Severity_at_Arraign", "supervision")] %>% felony_supervision.2020.01.01() %>% as.numeric()
  
  # Double checking section references
  result5 <- contains_any(x = data$Top_Arraign_Article_Section[index], patterns = qualifying.offenses.charge.2020.01.01) %>% as.numeric()
  
  # Tally all conditions
  result <- result1 + result2 + result3 + result4 + result5
  
  # Are any of the conditions satisfied? They are if the sum is greater than zero.
  result <- result > 0
  
  # Conver result to number and return
  result <- result %>% as.numeric()
  result %>% return()
}

# Run the function and get vector indicating whether the charge qualifies under the 2020.01.01 changes post facto. 
qualifyng.charges.2020.01.01.indicator <- sapply(X = 1:nrow(data.prelim), FUN = qualifyng.charges.2020.01.01.function)

# save(qualifyng.charges.2020.01.01.indicator,     file = "[2026.05.02] qualifyng.charges.2020.01.01.indicator.RData")

# load("[2026.03.10.1] qualifyng.charges.2020.01.01.indicator.RData")

```

## Append everything to make the qualifying charges vector. 

```{r}

# Clear environment
rm(list = ls())

library(dplyr)
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(sandwich)
library(readr)
library(lmtest)

# Create data.prelim object first.
# Load the data 

data.2020 <- read.csv("data.ny.2020.csv")
data.2021    <- read.csv("data.ny.2021.csv")
data.2022   <- read.csv("data.ny.2022.csv")
data.2023       <- read.csv("data.ny.2023.csv")
data.2024   <- read.csv("data.ny.2024.csv")
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2021 <- read_csv(
#   "data.ny.2021.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2022 <- read_csv(
#   "data.ny.2022.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2023 <- read_csv(
#   "data.ny.2023.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# data.2024 <- read_csv(
#   "data.ny.2024.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )

# Combine the data 
data <- rbind(data.2020, data.2021, data.2022, data.2023, data.2024)


# # Debugging
# library(readr)
# data.2020 <- read_csv(
#   "data.ny.2020.csv",
#   show_col_types = FALSE,
#   progress = TRUE
# )
# 
# nrow(data.2020)
# problems(data.2020)



# Create the different varibles.

# failure to appear
w <- toupper(trimws(data$Warrant_Ordered_btw_Arraign_and_Dispo))
d <- data$Release.Decision.at.Arraign == "Disposed at arraign"
data$fta_flag <- ifelse(d, NA_real_, ifelse(w == "Y", 1, ifelse(w == "N", 0, NA_real_)))

# release decisions
data <- data %>%
  mutate(release_v1 = ifelse(
    Release.Decision.at.Arraign == "ROR" | Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v1: defendant considered release iff they are released unconditionally.

data <- data %>%
  mutate(release_v2 = ifelse(
    Release.Decision.at.Arraign %in% c("ROR", "Nonmonetary release") | # more lenient
      Bail_Set_and_Posted_at_Arraign == "Y",
    1, 0
  )) # release_v2: defendant considered release iff they are released with or without conditions.

# Force NA when disposed at arraignment or unknown
data <- data %>%
  mutate(
    release_v1 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v1),
    release_v2 = ifelse(Release.Decision.at.Arraign %in% c("Disposed at arraign", "Unknown"), NA_real_, release_v2)
  )

# Force FTA to NA when defendant was not released under release_v2 - COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
data <- data %>%
  mutate(
    fta_flag = ifelse(release_v2 == 0, NA_real_, fta_flag)
  )

# Set new data object
data.prelim <- data


# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail

#####

load("[2026.05.02] qualifyng.charges.2023.06.09.indicator.RData")
load("[2026.05.02] qualifyng.charges.2022.05.01.indicator.RData")
load("[2026.05.02] qualifyng.charges.2020.07.01.indicator.RData")
load("[2026.05.02] qualifyng.charges.2020.01.01.indicator.RData")

# Get violent felonies per section a.
qualifyng.charges.VFO <- data.prelim$Top_Charge_at_Arraign_Violent_Felony_Ind == "Y"
qualifyng.charges.VFO <- qualifyng.charges.VFO %>% as.numeric()

qualifying.charges.matrix <- cbind(
                                   qualifyng.charges.2023.06.09.indicator,
                                   qualifyng.charges.2022.05.01.indicator,
                                   qualifyng.charges.2020.07.01.indicator,
                                   qualifyng.charges.2020.01.01.indicator,
                                   qualifyng.charges.VFO)

# save(qualifying.charges.matrix, file = "[2026.05.02] qualifying.charges.matrix.RData")

qualifying.charges.any <- as.numeric(rowSums(qualifying.charges.matrix) > 0)

# save(qualifying.charges.any, file = "[2026.05.02] qualifying.charges.any.RData")
# load("[2026.05.02] qualifying.charges.any.RData")

data.prelim <- cbind(data.prelim, qualifying.charges.any)
```

# Calculating Aggregate FTA rates. 

## Non-Qualifying charges, FTA among those ROR. 
```{r}
data.prelim <- data

# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail

# load("[2026.03.10.1] qualifying.charges.any.RData") # old
load("[2026.05.02] qualifying.charges.any.RData")
data.prelim <- cbind(data.prelim, qualifying.charges.any)

process_release <- function(filter_qualifying = FALSE) {
  
  if (filter_qualifying) {
    
    # Keep only qualifying charges
    data.prelim <<- data.prelim[data.prelim$qualifying.charges.any == 1, ]
    
  } else {
    # Force FTA to NA when defendant was not released under release_v1 - you *MAY* WANT TO COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
  data.prelim <- data.prelim %>%
    mutate(
      fta_flag = ifelse(release_v1 == 0, NA_real_, fta_flag)
    )
    
    # Set release_v2 = release_v1 for non-qualifying
    idx <- data.prelim$qualifying.charges.any == 0
    data.prelim$release_v2[idx] <<- data.prelim$release_v1[idx]
    
    # Keep only non-qualifying
    data.prelim <<- data.prelim[idx, ]
  }
}

# Non-Qualifying offenses
process_release()

# Qualifying offenses
# process_release(TRUE)


# Filter out fewer than 100 cases. 
  ## get numbers
  judge_release_table.prelim <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
  ## judges with at least 100 cases (in the prelim table)
keep_judges <- judge_release_table.prelim %>%
  filter(n_cases >= 100) %>% # Standard
  # filter(n_cases >= 150) %>% # Robustness check - A.7
  # filter(n_cases >= 50) %>% # Robustness check - A.7
    pull(Judge_Name)

  ## filter data.prelim to only those judges
  data.prelim.100 <- data.prelim %>%
  filter(Judge_Name %in% keep_judges)
  
  ## complete the filtering
  data.prelim <- data.prelim.100
  
# Overall FTA rate among defendants released under release_v1
fta_rate_release_v1 <- data.prelim %>%
  filter(release_v1 == 1) %>%
  summarise(
    n_released = n(),
    n_nonmissing_fta = sum(!is.na(fta_flag)),
    n_fta = sum(fta_flag == 1, na.rm = TRUE),
    fta_rate = mean(fta_flag, na.rm = TRUE) * 100
  )

fta_rate_release_v1
```

## Non-Qualifying charges, FTA among those Released with conditions. 
```{r}
data.prelim <- data

# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail

# load("[2026.03.10.1] qualifying.charges.any.RData") # old
load("[2026.05.02] qualifying.charges.any.RData")
data.prelim <- cbind(data.prelim, qualifying.charges.any)

process_release <- function(filter_qualifying = FALSE) {
  
  if (filter_qualifying) {
    
    # Keep only qualifying charges
    data.prelim <<- data.prelim[data.prelim$qualifying.charges.any == 1, ]
    
  } else {
  #   # Force FTA to NA when defendant was not released under release_v1 - you *MAY* WANT TO COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
  # data.prelim <- data.prelim %>%
  #   mutate(
  #     fta_flag = ifelse(release_v1 == 0, NA_real_, fta_flag)
  #   )
    
    # Set release_v2 = release_v1 for non-qualifying
    idx <- data.prelim$qualifying.charges.any == 0
    # data.prelim$release_v2[idx] <<- data.prelim$release_v1[idx]
    
    # Keep only non-qualifying
    data.prelim <<- data.prelim[idx, ]
  }
}

# Non-Qualifying offenses
process_release()

# Qualifying offenses
# process_release(TRUE)


# Filter out fewer than 100 cases. 
  ## get numbers
  judge_release_table.prelim <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
  ## judges with at least 100 cases (in the prelim table)
keep_judges <- judge_release_table.prelim %>%
  filter(n_cases >= 100) %>% # Standard
  # filter(n_cases >= 150) %>% # Robustness check - A.7
  # filter(n_cases >= 50) %>% # Robustness check - A.7
    pull(Judge_Name)

  ## filter data.prelim to only those judges
  data.prelim.100 <- data.prelim %>%
  filter(Judge_Name %in% keep_judges)
  
  ## complete the filtering
  data.prelim <- data.prelim.100
  
# Overall FTA rate among defendants released under release_v2 but not release_v1
# i.e., released with conditions / nonmonetary release
fta_rate_release_v2_not_v1 <- data.prelim %>%
  filter(release_v2 == 1, release_v1 == 0) %>%
  summarise(
    n_released_v2_not_v1 = n(),
    n_nonmissing_fta = sum(!is.na(fta_flag)),
    n_fta = sum(fta_flag == 1, na.rm = TRUE),
    fta_rate = mean(fta_flag, na.rm = TRUE) * 100
  )

fta_rate_release_v2_not_v1
```

## Qualifying charges, FTA among those ROR. 
```{r}
data.prelim <- data

# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail

# load("[2026.03.10.1] qualifying.charges.any.RData") # old
load("[2026.05.02] qualifying.charges.any.RData")
data.prelim <- cbind(data.prelim, qualifying.charges.any)

process_release <- function(filter_qualifying = FALSE) {
  
  if (filter_qualifying) {
    
    # Keep only qualifying charges
    data.prelim <<- data.prelim[data.prelim$qualifying.charges.any == 1, ]
    
  } else {
    # Force FTA to NA when defendant was not released under release_v1 - you *MAY* WANT TO COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
  data.prelim <- data.prelim %>%
    mutate(
      fta_flag = ifelse(release_v1 == 0, NA_real_, fta_flag)
    )
    
    # Set release_v2 = release_v1 for non-qualifying
    idx <- data.prelim$qualifying.charges.any == 0
    data.prelim$release_v2[idx] <<- data.prelim$release_v1[idx]
    
    # Keep only non-qualifying
    data.prelim <<- data.prelim[idx, ]
  }
}

# # Non-Qualifying offenses
# process_release()

# Qualifying offenses
process_release(TRUE)


# Filter out fewer than 100 cases. 
  ## get numbers
  judge_release_table.prelim <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
  ## judges with at least 100 cases (in the prelim table)
keep_judges <- judge_release_table.prelim %>%
  filter(n_cases >= 100) %>% # Standard
  # filter(n_cases >= 150) %>% # Robustness check - A.7
  # filter(n_cases >= 50) %>% # Robustness check - A.7
    pull(Judge_Name)

  ## filter data.prelim to only those judges
  data.prelim.100 <- data.prelim %>%
  filter(Judge_Name %in% keep_judges)
  
  ## complete the filtering
  data.prelim <- data.prelim.100
  
# Overall FTA rate among defendants released under release_v1
fta_rate_release_v1 <- data.prelim %>%
  filter(release_v1 == 1) %>%
  summarise(
    n_released = n(),
    n_nonmissing_fta = sum(!is.na(fta_flag)),
    n_fta = sum(fta_flag == 1, na.rm = TRUE),
    fta_rate = mean(fta_flag, na.rm = TRUE) * 100
  )

fta_rate_release_v1
```


## Qualifying charges, FTA among those Released with conditions. 
```{r}
data.prelim <- data

# Remove cases with nominal $1 bail (often used to credit time served on a different case)
data.prelim <- data.prelim %>%
  filter(Region == "NYC") %>%            # keep only NYC cases
  filter(First_Bail_Set_Cash != 1 | is.na(First_Bail_Set_Cash))  # exclude $1 cash bail

# load("[2026.03.10.1] qualifying.charges.any.RData") # old
load("[2026.05.02] qualifying.charges.any.RData")
data.prelim <- cbind(data.prelim, qualifying.charges.any)

process_release <- function(filter_qualifying = FALSE) {
  
  if (filter_qualifying) {
    
    # Keep only qualifying charges
    data.prelim <<- data.prelim[data.prelim$qualifying.charges.any == 1, ]
    
  } else {
  #   # Force FTA to NA when defendant was not released under release_v1 - you *MAY* WANT TO COMMENT OUT IF FOCUSING ON QUALIFYING CHARGES.
  # data.prelim <- data.prelim %>%
  #   mutate(
  #     fta_flag = ifelse(release_v1 == 0, NA_real_, fta_flag)
  #   )
    
    # Set release_v2 = release_v1 for non-qualifying
    idx <- data.prelim$qualifying.charges.any == 0
    # data.prelim$release_v2[idx] <<- data.prelim$release_v1[idx]
    
    # Keep only non-qualifying
    data.prelim <<- data.prelim[idx, ]
  }
}

# # Non-Qualifying offenses
# process_release()

# Qualifying offenses
process_release(TRUE)


# Filter out fewer than 100 cases. 
  ## get numbers
  judge_release_table.prelim <- data.prelim %>%
  group_by(Judge_Name) %>%
  summarise(
    n_cases = n(), # [2025.12.18] number of cases
    pct_release_v1 = mean(release_v1, na.rm = TRUE) * 100,
    pct_release_v2 = mean(release_v2, na.rm = TRUE) * 100
  )
  
  ## judges with at least 100 cases (in the prelim table)
keep_judges <- judge_release_table.prelim %>%
  filter(n_cases >= 100) %>% # Standard
  # filter(n_cases >= 150) %>% # Robustness check - A.7
  # filter(n_cases >= 50) %>% # Robustness check - A.7
    pull(Judge_Name)

  ## filter data.prelim to only those judges
  data.prelim.100 <- data.prelim %>%
  filter(Judge_Name %in% keep_judges)
  
  ## complete the filtering
  data.prelim <- data.prelim.100
  
# Overall FTA rate among defendants released under release_v2 but not release_v1
# i.e., released with conditions / nonmonetary release
fta_rate_release_v2_not_v1 <- data.prelim %>%
  filter(release_v2 == 1, release_v1 == 0) %>%
  summarise(
    n_released_v2_not_v1 = n(),
    n_nonmissing_fta = sum(!is.na(fta_flag)),
    n_fta = sum(fta_flag == 1, na.rm = TRUE),
    fta_rate = mean(fta_flag, na.rm = TRUE) * 100
  )

fta_rate_release_v2_not_v1
```







